### 2022-02-19 Articles.Rmd
updated legend and axis's

---
title: "Articles_Plots"
author: "Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 14,fig.height = 16,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)

```

# Using Normal Distribution for Data

```{r Load data model 1}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("DM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r Load data model 2}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("DM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r Load data model 3}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("DM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r Load data model 4}
# Random Sampling
load(here("Non_Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))

Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("DM",paste0("AM ",1:3))

for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Info<-All_Info
RS_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# All elements
All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",All_MSE))

remove(All_Info,All_MSE,RS_Info,RS_MSE)
```

```{r combine data and plot,fig.width = 18,fig.height = 10}
Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
                    M3_Identical_r0,M4_Identical_r0)

Identical_ro$Covariate<-factor(Identical_ro$Covariate,
                               levels = c("X1, X2","X1, X2, X1\u00B2",
                                          "X1, X2, X2\u00B2","X1, X2, X1\u00B2, X2\u00B2"))

Identical_ro$Model<-factor(Identical_ro$Model,
                           levels = c("RS DM","RS AM 1","RS AM 2","RS AM 3",
                                      "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
                                      "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
                                      "mMSE MR","mVc MR"))

Selected_Models_mMSE<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
                        "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
                        "mMSE MR")

Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
               "#FFC4D8", "#E28490","#BB2C3E","#55141C",
               "#DDCC77")

Selected_Models_mVc<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
                       "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
                       "mVc MR")

Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
                          "#FFC4D8","#E28490","#BB2C3E","#55141C", 
                          "#DDCC77")

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank())->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank())->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank())->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab("Sub-sample size")+ylab("SMSE")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        panel.grid.minor.x = element_blank())->p4

ggarrange(p1,p3,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
ggarrange(p2,p4,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
```

### 2022-04-04 Articles.Rmd
Update article file and gifski package

@@
 ```{r Load data model 1}
+load(here("Identical_r0","Generate_Big_Data","Model_1","No_Correlated_Covariate.RData"))
+Model_1_SS<-r0
+
+remove(Simulated_Data,Model_1,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M1_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2",Metric="MSE",All_MSE))
+M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M1_Identical_r0$Subsample_Size<-M1_Identical_r0$Subsample_Size-Model_1_SS
 ```
@@
 ```{r Load data model 2}
+load(here("Identical_r0","Generate_Big_Data","Model_2","No_Correlated_Covariate.RData"))
+Model_2_SS<-r0
+
+remove(Simulated_Data,Model_2,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M2_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2, X1\u00B2",Metric="MSE",All_MSE))
+M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M2_Identical_r0$Subsample_Size<-M2_Identical_r0$Subsample_Size-Model_2_SS
 ```
@@
 ```{r Load data model 3}
+load(here("Identical_r0","Generate_Big_Data","Model_3","No_Correlated_Covariate.RData"))
+Model_3_SS<-r0
+
+remove(Simulated_Data,Model_3,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M3_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2, X2\u00B2",Metric="MSE",All_MSE))
+M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M3_Identical_r0$Subsample_Size<-M3_Identical_r0$Subsample_Size-Model_3_SS
 ```
@@
 ```{r Load data model 4}
+load(here("Identical_r0","Generate_Big_Data","Model_4","No_Correlated_Covariate.RData"))
+Model_4_SS<-r0
+
+remove(Simulated_Data,Model_4,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+
 # Random Sampling
@@
 
-M4_Identical_r0<-rbind(cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",All_Info),
-                       cbind.data.frame(Covariate="X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",All_MSE))
+M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",
+                                        All_Info),
+                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",
+                                        All_MSE))
 
 remove(All_Info,All_MSE,RS_Info,RS_MSE)
+
+M4_Identical_r0$Subsample_Size<-M4_Identical_r0$Subsample_Size-Model_4_SS
 ```
@@
 Identical_ro$Covariate<-factor(Identical_ro$Covariate,
-                               levels = c("X1, X2","X1, X2, X1\u00B2",
-                                          "X1, X2, X2\u00B2","X1, X2, X1\u00B2, X2\u00B2"))
+                               levels = c("Data Model: X1, X2",
+                                          "Data Model: X1, X2, X1\u00B2",
+                                          "Data Model: X1, X2, X2\u00B2",
+                                          "Data Model: X1, X2, X1\u00B2, X2\u00B2"))
 
@@
                                       "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                                      "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
+                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
                                       "mMSE MR","mVc MR"))
 
-Selected_Models_mMSE<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
-                        "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                        "mMSE MR")
+Identical_ro$Model<-recode_factor(Identical_ro$Model,
+                                  `RS DM`="Random Sampling: Data Model",
+                                  `RS AM 1`="Random Sampling: Incorrect Model 1",
+                                  `RS AM 2`="Random Sampling: Incorrect Model 2",
+                                  `RS AM 3`="Random Sampling: Incorrect Model 3",
+                                  `mMSE DM`="Optimal Sub-sampling mMSE: Data Model",
+                                  `mMSE AM 1`="Optimal Sub-sampling mMSE: Incorrect Model 1",
+                                  `mMSE AM 2`="Optimal Sub-sampling mMSE: Incorrect Model 2",
+                                  `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
+                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model 1",
+                                  `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
+                                  `mVc AM 2`="Optimal Sub-sampling mVc: Incorrect Model 2",
+                                  `mVc AM 3`="Optimal Sub-sampling mVc: Incorrect Model 3",
+                                  `mMSE MR`="Model Robust Optimal Sub-sampling mMSE: Data Model",
+                                  `mVc MR`="Model Robust Optimal Sub-sampling mVc: Data Model")
+
+Selected_Models_mMSE<-c("Random Sampling: Data Model",
+                        #"Random Sampling: Incorrect Model 1",
+                        #"Random Sampling: Incorrect Model 2",
+                        #"Random Sampling: Incorrect Model 3",
+                        "Optimal Sub-sampling mMSE: Data Model",
+                        "Optimal Sub-sampling mMSE: Incorrect Model 1",
+                        "Optimal Sub-sampling mMSE: Incorrect Model 2",
+                        "Optimal Sub-sampling mMSE: Incorrect Model 3",
+                        "Model Robust Optimal Sub-sampling mMSE: Data Model")
 
@@
 
-Selected_Models_mVc<-c("RS DM",#"RS AM 1","RS AM 2","RS AM 3",
-                       "mVc DM", "mVc AM 1", "mVc AM 2","mVc AM 3",
-                       "mVc MR")
+Selected_Models_mVc<-c("Random Sampling: Data Model",
+                       #"Random Sampling: Incorrect Model 1",
+                       #"Random Sampling: Incorrect Model 2",
+                       #"Random Sampling: Incorrect Model 3",
+                       "Optimal Sub-sampling mVc: Data Model 1",
+                       "Optimal Sub-sampling mVc: Incorrect Model 1",
+                       "Optimal Sub-sampling mVc: Incorrect Model 2",
+                       "Optimal Sub-sampling mVc: Incorrect Model 3",
+                       "Model Robust Optimal Sub-sampling mVc: Data Model")
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mMSE
+
+Temp_legend_mMSE<-get_legend(Temp_plot_mMSE)
+
+Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mVc
+
+Temp_legend_mVc<-get_legend(Temp_plot_mVc)
+
+Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p1
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
+
+Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("Model Information")+expand_limits(y = 0)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p2
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p2
 
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab("Sub-sample size")+ylab("SMSE")+expand_limits(y = 0)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("SMSE")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p3
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p3
 
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank())->p4
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p4
 
-ggarrange(p1,p3,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
-ggarrange(p2,p4,nrow = 2,ncol = 1,common.legend = TRUE,legend = "right")
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
 ```

### 2022-04-09 Articles.Rmd
SMSE and model information stored as pdfs

@@
 
-M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2",Metric="Model Information",
+M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                         All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2",Metric="MSE",
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                         All_MSE))
@@
 
-M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="Model Information",
+M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                         All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2",Metric="MSE",
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                         All_MSE))
@@
 
-M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="Model Information",
+M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                         All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2, X2\u00B2",Metric="MSE",
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                         All_MSE))
@@
 
-M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="Model Information",
-                                        All_Info),
-                       cbind.data.frame(Covariate="Data Model: X1, X2, X1\u00B2, X2\u00B2",Metric="MSE",
-                                        All_MSE))
+M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="Model Information",All_Info),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="MSE",All_MSE))
 
@@
 
-```{r combine data and plot,fig.width = 18,fig.height = 10}
+```{r combine data and plot,fig.width = 8,fig.height = 12}
 Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
@@
 Identical_ro$Covariate<-factor(Identical_ro$Covariate,
-                               levels = c("Data Model: X1, X2",
-                                          "Data Model: X1, X2, X1\u00B2",
-                                          "Data Model: X1, X2, X2\u00B2",
-                                          "Data Model: X1, X2, X1\u00B2, X2\u00B2"))
+                               levels = c("Data Model: x\u2081, x\u2082",
+                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",
+                                          "Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",
+                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"))
 
@@
 Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
-               "#FFC4D8", "#E28490","#BB2C3E","#55141C",
+               "#FFC4D8","#E28490","#BB2C3E","#55141C",
                "#DDCC77")
@@
 
+#Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]
+
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
@@
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
   xlab(expression(paste(r[0],' = 100 and r')))+
@@
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
   xlab(expression(paste(r[0],' = 100 and r')))+
@@
 
-ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
-ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
+
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
+  ggexport(filename = "SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
+  ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
 ```

### 2022-06-02 Articles.Rmd
update colors for the plots

@@
                                   `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
-                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model 1",
+                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model",
                                   `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
@@
 
-Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
-               "#FFC4D8","#E28490","#BB2C3E","#55141C",
-               "#DDCC77")
+# Colors_mMSE<-c("#88CCEE", #"#A6C3D3","#5D92B0","#35586C", 
+#                "#FFC4D8","#E28490","#BB2C3E","#55141C",
+#                "#DDCC77")
+
+Colors_mMSE<-c("black",#"grey","grey","grey",
+              "#cc0000", 
+              "#ff578a","#ff578a","#ff578a",
+              "darkgreen")
 
@@
                        #"Random Sampling: Incorrect Model 3",
-                       "Optimal Sub-sampling mVc: Data Model 1",
+                       "Optimal Sub-sampling mVc: Data Model",
                        "Optimal Sub-sampling mVc: Incorrect Model 1",
@@
 
-Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
-                          "#FFC4D8","#E28490","#BB2C3E","#55141C", 
-                          "#DDCC77")
+# Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
+#                           "#FFC4D8","#E28490","#BB2C3E","#55141C", 
+#                           "#DDCC77")
+
+Colors_mVc<-c("black",#"grey","grey","grey",
+              "#cc0000", 
+              "#ff578a","#ff578a","#ff578a",
+              "darkgreen")
 

### 2022-06-24 Manual.Rmd
Added manual with diagrams

---
title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for PoissonRegression (standardised Multivariate Normal Distribution)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Overview

* The project ***"Normal_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Normal"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the Poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.

* This document aims to state every important part of this R project thoroughly in terms of folder structure related to used sub-sampling methods.

# 2. Folder structure

![](Images/FullDiagram.png)

* The sub-sampling methods applied in this study are 
1. Random Sampling, 
2. Rare event random sampling, 
3. Optimal Sub-sampling (OSMAC), and
4. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).

* A detailed description of all methods are explained in the Figure below.

![](Images/All Methods Figure.png)

* Simulations are repeated ***Replicates*** times such that at each replicate only ***Subsample_Size*** data points are extracted from the Big Data set of ***N*** observations. It is necessary to have replications so that we can evaluate the methods through MSE and model information of the estimated model parameters.

* The results from this simulation setup are stored in a such way that they could be summarised through Rmarkdown files for individual or grouped assessment for the above mentioned methods.

* In optimal sub-sampling and model robust optimal sub-sampling an initial sub-sample of **r0** observations are used to estimate the model parameters of a given model. From these parameters only the sub-sampling probabilities are calculated. Therefore, to compare optimal sub-sampling with model robust optimal sub-sampling there are two options; 1). Identical **r0** and 2). Non-Identical **r0**.

* Hence, **Identical_r0** can be used for method comparison and **Non_Identical_r0** can be used for application purposes.

## 2.1 Generated_Big_Data

![](Images/Generate_Big_Data.png)

* Generate and store Big Data.

* Based on the real model of the Poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Normal_Special.R***.

* To ensure that the data generated from the true model performs better than the assumed models run ***Check_Data.Rmd*** and look at the plots stored as **Model_[1 or 2 or 3 or 4]_X[1 or 2]**.

* In the Rscript, ***Replicates*** - number of unique simulations, ***Subsample_Size*** - target sample size, ***N*** - Big data size, ***Theta*** - Real model parameters, ***r0*** - initial sample size for optimal and model robust optimal sub-sampling.

* As of now the model parameters and their respective response compositions are 
1. $\theta=[-1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
2. $\theta=[-1.0, 0.5, 0.5, 0.7]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
3. $\theta=[-1.0, 0.5, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
4. $\theta=[-1.0, 0.5, 0.5, 0.5, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.

* For each model structure covariate data was generated only through zero covariance matrices with mean of zeros from the Multivariate Normal distribution.

## 2.2 Simulation_Setup

![](Images/Simulation_Setup.png)

* Contains the simulation setup for the above mentioned subsampling methods based on the variety of Big data sets and Rscripts to smoothly transfer methods and respective data based on real models.

### 2.2.1 Classical/R_Scripts

We need to transfer two forms of data,
1. Big Data set and other information essential for the methods.
2. Functions for the sub-sampling methods.

* Here we develop the functions and transfer them safely to the simulation setup.

#### 2.2.1.1 Setup_Data.R

* Data stored in **Generate_Big_Data** is transferred to **Classical/Analysis**.

#### 2.2.1.2 Random_Sampling_Setup.R

* A setup for random sampling such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.3 RE Random_Sampling_Setup.R

* A setup for rare event random sampling such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]

* The optimal sub-sampling, model robust optimal sub-sampling and a setup to apply these methods such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]

* The optimal sub-sampling and a setup to apply these methods such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

#### 2.2.1.6 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]

* The model robust optimal sub-sampling and a setup to apply these methods such that model parameters and model information are estimated at each simulation and are applied for the generated big data.

## 2.2.2 Classical/Analysis

Each model related covariate data is separately used on each subsampling method individually.

#### 2.2.2.1 Random Sampling

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_RandomSample.RData** - Random sampling function for **Replicates**.
* **Simulation_Results_Random_Sampling.R** - R script to run the random sampling method over **Replicates** on the **Init.RData** from **Run_RandomSample.RData**.
* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **Random_Sample_output.RData** is stored.

#### 2.2.2.2 RE Random Sampling

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **RE_RandomSample.RData** - RE Random sampling function for **Replicates**.
* **Simulation_Results_RE_Random_Sampling.R** - R script to run the rare event random sampling method over **Replicates** on the **Init.RData** from **RE_RandomSample.RData**.
* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **RE_Random_Sample_output.RData** is stored.

#### 2.2.2.3 OSMAC [Non Identical r0]

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_OSMAC.RData** - Optimal sampling function for **Replicates**.
* **Simulation_Results_OSMAC_Sampling.R** - R script to run the optimal sampling method over **Replicates** on the **Init.RData** from **Run_OSMAC.RData**.
* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **OSMAC_output.RData** is stored.

#### 2.2.2.4 OSMAC Model Free [Non Identical r0]

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_OSMAC.RData** - model robust optimal sampling function for **Replicates**.
* **Simulation_Results_OSMAC_Sampling.R** - R script to run the model robust optimal sampling method over **Replicates** on the **Init.RData** from **Run_OSMAC.RData**.
* **Results** - Results of the simulation are stored here as a single Rdata file **OSMAC_MF_output.RData**.

#### 2.2.2.5 OSMAC [Identical r0]

* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
* **Run_OSMAC.RData** - optimal sampling and model robust optimal sampling function for **Replicates**.
* **Simulation_Results_OSMAC_Sampling.R** - R script to run the optimal sampling and model robust optimal sampling methods over **Replicates** on the **Init.RData** from **Run_OSMAC.RData**.
* **Results** - Results of the simulation are stored here according to real models, assumed models and model robust (free) methods in each folder as Rdata files **OSMAC_output.RData**.

## 2.3 Outputs

* While in the **Simulation_Setup** results are stored for analysis purposes, the same results are stored here.

![](Images/Outputs.png)

## 2.4 Rmarkdown

![](Images/Rmarkdown.png)

* Rmarkdown files are used to individually assess the sub-sampling methods through plots for estimated model parameters, variance and bias.

* **RE_and_Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.

* **OSMAC_Command.R** - R script to summarise the results from the optimal sub-sampling and model robust optimal sampling methods through the Rmarkdown file **OSMAC_Method.Rmd**.

* **Summary_Rmarkdown.R** in the **Rmarkdown/Classical/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.

## 2.5 htmloutputs

![](Images/htmloutputs.png)

* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.

## 2.6 Summary

![](Images/Summary.png)

* Here, summaries from the Rmarkdown files **Best_Subsampling_Method.Rmd** are stored as html files.

### 2.6.1 Summary/Classical/Model_[1 or 2 or 3 or 4]/Data/Efficiency

* When running the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.

* Using these data files only summarising through the files in **Rmarkdown/Classical/Summary** occurs.

## 2.7 Articles.Rmd, Publication.Rmd and Publication_Ready_Command.R

* Use **Publication_Ready_command.R** to run **Publication.Rmd** on every model and its respective big data.

* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_PR_TV_Nor_mMSE.pdf** and **SMSE_MI_PR_TV_Nor_mVc.pdf**.

### 2022-06-24 Manual.Rmd
updated manual title spelling mistakes

@@
 ---
-title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for PoissonRegression (standardised Multivariate Normal Distribution)"
+title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)"
 output: github_document
@@
 
-* The project ***"Normal_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Normal"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the Poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.
+* The project ***"Normal_Distribution"*** or ***"RS_OS_MROS_PR_TwoVar_Normal"*** is developed for the purpose of conducting a simulation study such that estimated model parameters of the poisson regression model can be compared through the obtained informative samples from the Big Data using optimal sub-sampling and model robust optimal sub-sampling methods.
 
@@
 
-* Based on the real model of the Poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Normal_Special.R***.
+* Based on the real model of the poisson regression data we have four folders and in each folder their respective Big Data sets are stored by using ***Checking_SP_Model_1_Normal_Special.R***.
 
@@
 
-* For each model structure covariate data was generated only through zero covariance matrices with mean of zeros from the Multivariate Normal distribution.
+* For each model structure covariate data was generated only through standardised Multivariate Normal distribution.
 
@@
 
-#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]
+#### 2.2.1.5 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]
 

### 2022-06-25 Manual.Rmd
updated theta values for the models
output clarification for OSMAC added

@@
 * As of now the model parameters and their respective response compositions are 
-1. $\theta=[-1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
-2. $\theta=[-1.0, 0.5, 0.5, 0.7]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
-3. $\theta=[-1.0, 0.5, 0.5, 0.3]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
-4. $\theta=[-1.0, 0.5, 0.5, 0.5, 0.5]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.
+1. $\theta=[1.0, 0.5, 0.1]$ generates data for Model 1 of $x_1,x_2$.
+2. $\theta=[1.0,-0.3, 0.3, 0.1]$ generates data for Model 2 of $x_1,x_2,x^2_1$.
+3. $\theta=[1.0, 0.3,-0.3, 0.1]$ generates data for Model 3 of $x_1,x_2,x^2_2$.
+4. $\theta=[1.0, 0.3, 0.3,-0.3, 0.1]$ generates data for Model 4 of $x_1,x_2,x^2_1,x^2_2$.
 
@@
 
+* In **Identical_r0** for OSMAC Assumed Models there are two forms of outputs, 1) **OSMAC_output_New_x.Rdata** is when optimal sub-sampling probabilities are selected from the re-calculated probabilities of the Data Generating model, 2) **OSMAC_output_Old_x.Rdata** is when optimal sub-sampling probabilities are calculated based on the Assumed model.
+Throughout the simulation setup the later output is used.
+
 ![](Images/Outputs.png)

### 2022-06-27 Manual.Rmd
updated manual and readme file with diagrams and brief summary

@@
 title: "Manual of comparing optimal subsampling with model robust optimal subsampling method for poisson regression (standardised Multivariate Normal distribution)"
-output: github_document
+output: 
+  html_document:
+    keep_md: yes
 ---

### 2022-06-28 Non_Identical_r0/Rmarkdown/Classical/Random_Sampling_And_OSMAC.R
update R code with date and Model 1

@@ -6,29 +6,29 @@ Model<-c("Model_1","Model_2",
          "Model_3","Model_4") ; j=4
 
 # Random Sampling ----
-ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Random_Sampling.Rmd"),
-       out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"Random_Sampling"),
-       fig_dir = c("Plots"),
-       params=list("Model_Path"=Model[j]),
-       verbose = TRUE,keep_md = FALSE)
-open_output_dir()
-
 for (j in 1:length(Model)) 
 {
-        # OSMAC Method ----
-        ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
-               out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
-               fig_dir = c("Plots"),
-               params=list("Model_Path"=Model[j]),
-               verbose = TRUE,keep_md = FALSE)
-        #open_output_dir()
-        
-        # OSMAC Model Free Method ----
-        ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Model_Free_Method.Rmd"),
-               out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC_Model_Free"),
-               fig_dir = c("Plots"),
-               params=list("Model_Path"=Model[j]),
-               verbose = TRUE,keep_md = FALSE)
-        #open_output_dir()
+  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Random_Sampling.Rmd"),
+         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"Random_Sampling"),
+         fig_dir = c("Plots"),
+         params=list("Model_Path"=Model[j]),
+         verbose = TRUE,keep_md = FALSE)
+  #open_output_dir()
+  
+  # OSMAC Method ----
+  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
+         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
+         fig_dir = c("Plots"),
+         params=list("Model_Path"=Model[j]),
+         verbose = TRUE,keep_md = FALSE)
+  #open_output_dir()
+  
[…]

### 2022-09-27 Articles.Rmd
Additionally calculate Average MSE Y for the existing results

@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
 }
@@
 RS_MSE<-All_MSE
+RS_ACC<-Accuracy_Data
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
+All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]
 
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
 }
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
 }
@@
 OSMAC_MSE<-All_MSE
+OSMAC_ACC<-All_ACC
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
 All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
+All_ACC<-rbind(RS_ACC,OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])
 
@@
 colnames(All_MSE)[3]<-"Estimated Values"
+colnames(All_ACC)[3]<-"Estimated Values"
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
-                                        All_MSE))
+                                        All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
+                                        All_ACC))
 
-remove(All_Info,All_MSE,RS_Info,RS_MSE)
+remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)
 
@@
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
+Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]
 
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
 }
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
 }
@@
 OSMAC_MSE<-All_MSE
+OSMAC_ACC<-Accuracy_Data
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
-                                        All_MSE))
+                                        All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
+                                        All_ACC))
 
-remove(All_Info,All_MSE,RS_Info,RS_MSE)
+remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)
 
@@
 OSMAC_MSE<-All_MSE
+OSMAC_ACC<-All_ACC
 
-remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)
+remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,All_ACC)
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
-                                        All_MSE))
+                                        All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
+                                        All_ACC))
 
@@
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
-                                        Metric="MSE",All_MSE))
+                                        Metric="MSE",All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="Average MSE Y",All_ACC))
 
-remove(All_Info,All_MSE,RS_Info,RS_MSE)
+remove(All_Info,All_MSE,RS_Info,RS_MSE,RS_ACC)
 
@@
 
-Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
-                     breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
-  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
-
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
@@
 
+Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Average MSE Y")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p5
+
+Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab(expression(paste(r[0],' = 100 and r')))+
+  ylab("Average MSE Y")+expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
+        panel.grid.minor.x = element_blank(),
+        axis.title.x = element_text(color = "black",face = "bold",size = 12),
+        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p6
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
+ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
+ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
 
@@
   ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
+ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_LR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_LR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
 ```

### 2022-09-27 Articles.Rmd
Delete files

@@
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_LR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = "ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_LR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = "ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
 ```

### 2022-10-03 Articles.Rmd
plots are updated for visibility

@@
 
+Theme_special<-function()
+{
+  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
+        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
+        strip.text = element_text(colour = "black",size = 12,face="bold"),
+        panel.grid.minor.x = element_blank(),
+        axis.title= element_text(color = "black",face = "bold",size = 12),
+        legend.text = element_text(color = "black", size=11),
+        legend.position = "bottom",
+        legend.margin=margin(0,0,0,0),
+        legend.box.margin=margin(-1,-2,-1,-2)) 
+}
+
 #Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mMSE
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->Temp_plot_mVc
+  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p1
+  theme_bw()+Theme_special()->p1
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Model Information")+expand_limits(y = 0)+
+  ylab("Average Model Information")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p2
+  theme_bw()+Theme_special()->p2
 
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p3
+  theme_bw()+Theme_special()->p3
 
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p4
+  theme_bw()+Theme_special()->p4
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Average MSE Y")+expand_limits(y = 0)+
+  ylab("Average MSE of Y")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p5
+  theme_bw()+Theme_special()->p5
 
@@
   xlab(expression(paste(r[0],' = 100 and r')))+
-  ylab("Average MSE Y")+expand_limits(y = 0)+
+  ylab("Average MSE of Y")+expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
-        panel.grid.minor.x = element_blank(),
-        axis.title.x = element_text(color = "black",face = "bold",size = 12),
-        axis.title.y = element_text(color = "black",face = "bold",size = 12))->p6
+  theme_bw()+Theme_special()->p6
 

### 2022-10-03 Articles.Rmd
x axis title changed to r

@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("SMSE")+expand_limits(y = 0)+
@@
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' = 100 and r')))+
+  xlab("r")+
   ylab("Average MSE of Y")+expand_limits(y = 0)+

### 2022-10-11 Articles.Rmd
y axis scaled to log and log10

@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("Average Model Information")+expand_limits(y = 0)+
+  ylab("log10(Average Model Information)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("SMSE")+expand_limits(y = 0)+
+  ylab("log(SMSE)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("Average MSE of Y")+expand_limits(y = 0)+
+  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),

### 2022-10-13 Articles.Rmd
log10 to log for uniformity

@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   xlab("r")+
-  ylab("log10(Average Model Information)")+#expand_limits(y = 0)+
+  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log10(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),

### 2022-11-05 Articles.Rmd
eps files stored

@@
 
+# ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
+#   ggexport(filename = "SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
+# ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
+#   ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
+# ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+#   ggexport(filename = "ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+# ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+#   ggexport(filename = "ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
+  ggsave(filename = "SMSE_MI_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-  ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
+  ggsave(filename = "SMSE_MI_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+  ggsave(filename = "ACCURACY_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+  ggsave(filename = "ACCURACY_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
 ```

### 2022-12-15 Articles.Rmd
update labels subsampling

@@
 
-remove(Simulated_Data,Model_1,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
 
-remove(Simulated_Data,Model_2,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
 
-remove(Simulated_Data,Model_3,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
 
-remove(Simulated_Data,Model_4,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
+remove(Simulated_Data,Nc_size,r0,Replicates,Subsample_Size,Model_Path)
 
@@
                                   `RS AM 3`="Random Sampling: Incorrect Model 3",
-                                  `mMSE DM`="Optimal Sub-sampling mMSE: Data Model",
-                                  `mMSE AM 1`="Optimal Sub-sampling mMSE: Incorrect Model 1",
-                                  `mMSE AM 2`="Optimal Sub-sampling mMSE: Incorrect Model 2",
-                                  `mMSE AM 3`="Optimal Sub-sampling mMSE: Incorrect Model 3",
-                                  `mVc DM`="Optimal Sub-sampling mVc: Data Model",
-                                  `mVc AM 1`="Optimal Sub-sampling mVc: Incorrect Model 1",
-                                  `mVc AM 2`="Optimal Sub-sampling mVc: Incorrect Model 2",
-                                  `mVc AM 3`="Optimal Sub-sampling mVc: Incorrect Model 3",
-                                  `mMSE MR`="Model Robust Optimal Sub-sampling mMSE: Data Model",
-                                  `mVc MR`="Model Robust Optimal Sub-sampling mVc: Data Model")
+                                  `mMSE DM`="Optimal subsampling mMSE: Data Model",
+                                  `mMSE AM 1`="Optimal subsampling mMSE: Incorrect Model 1",
+                                  `mMSE AM 2`="Optimal subsampling mMSE: Incorrect Model 2",
+                                  `mMSE AM 3`="Optimal subsampling mMSE: Incorrect Model 3",
+                                  `mVc DM`="Optimal subsampling mVc: Data Model",
+                                  `mVc AM 1`="Optimal subsampling mVc: Incorrect Model 1",
+                                  `mVc AM 2`="Optimal subsampling mVc: Incorrect Model 2",
+                                  `mVc AM 3`="Optimal subsampling mVc: Incorrect Model 3",
+                                  `mMSE MR`="Model Robust subsampling mMSE: Data Model",
+                                  `mVc MR`="Model Robust subsampling mVc: Data Model")
 
@@
                         #"Random Sampling: Incorrect Model 3",
-                        "Optimal Sub-sampling mMSE: Data Model",
-                        "Optimal Sub-sampling mMSE: Incorrect Model 1",
-                        "Optimal Sub-sampling mMSE: Incorrect Model 2",
-                        "Optimal Sub-sampling mMSE: Incorrect Model 3",
-                        "Model Robust Optimal Sub-sampling mMSE: Data Model")
+                        "Optimal subsampling mMSE: Data Model",
+                        "Optimal subsampling mMSE: Incorrect Model 1",
+                        "Optimal subsampling mMSE: Incorrect Model 2",
+                        "Optimal subsampling mMSE: Incorrect Model 3",
+                        "Model Robust subsampling mMSE: Data Model")
 
@@
                        #"Random Sampling: Incorrect Model 3",
-                       "Optimal Sub-sampling mVc: Data Model",
-                       "Optimal Sub-sampling mVc: Incorrect Model 1",
-                       "Optimal Sub-sampling mVc: Incorrect Model 2",
-                       "Optimal Sub-sampling mVc: Incorrect Model 3",
-                       "Model Robust Optimal Sub-sampling mVc: Data Model")
+                       "Optimal subsampling mVc: Data Model",
+                       "Optimal subsampling mVc: Incorrect Model 1",
+                       "Optimal subsampling mVc: Incorrect Model 2",
+                       "Optimal subsampling mVc: Incorrect Model 3",
+                       "Model Robust subsampling mVc: Data Model")
 

### 2022-12-15 Articles.Rmd
updated pdf plots

@@
 
-# ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-#   ggexport(filename = "SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
-# ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-#   ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
-# ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-#   ggexport(filename = "ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
-# ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-#   ggexport(filename = "ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
+  ggexport(filename = "SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
+ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
+  ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
+ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
 

### 2023-02-11 Articles.Rmd
updated plots after adding MSE for MLE in rmarkdown files

@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
   Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
@@
 RS_MSE<-All_MSE
+RS_MSE_MLE<-All_MSE_MLE
 RS_ACC<-Accuracy_Data
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
   All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
   All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
@@
 OSMAC_MSE<-All_MSE
+OSMAC_MSE_MLE<-All_MSE_MLE
 OSMAC_ACC<-All_ACC
@@
 All_MSE<-rbind(RS_MSE,OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
+All_MSE_MLE<-rbind(RS_MSE_MLE,OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
 All_Info<-rbind(RS_Info,OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
@@
 colnames(All_MSE)[3]<-"Estimated Values"
+colnames(All_MSE_MLE)[3]<-"Estimated Values"
 colnames(All_ACC)[3]<-"Estimated Values"
@@
                                         All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE for MLE",
+                                        All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
   Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
@@
   All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
+  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
   Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
@@
 OSMAC_MSE<-All_MSE
+OSMAC_MSE_MLE<-All_MSE_MLE
 OSMAC_ACC<-Accuracy_Data
@@
 colnames(All_Info)[3]<-"Estimated Values"
+colnames(All_MSE_MLE)[3]<-"Estimated Values"
 colnames(All_MSE)[3]<-"Estimated Values"
@@
                                         All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE for MLE",
+                                        All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
                                         All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE for MLE",
+                                        All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
@@
 # Random Sampling
-load(here("Non_Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
+load(here("Non_Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_RS.RData"))
 
@@
 # OSMAC
-load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
+load(here("Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
 All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
+All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
 All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
@@
                                         Metric="MSE",All_MSE),
+                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
+                                        Metric="MSE for MLE",All_MSE_MLE),
                        cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
@@
 
+Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mMSE)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab("r")+
+  ylab("log(SMSE)")+#expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+Theme_special()->p7
+
+Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
+                     breaks = unique(Identical_ro$Subsample_Size))+
+  geom_point(size=1.75)+geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  xlab("r")+
+  ylab("log(SMSE)")+#expand_limits(y = 0)+
+  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
+  theme_bw()+Theme_special()->p8
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
@@
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
+ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
+ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
 
@@
 
+ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
@@
   ggsave(filename = "ACCURACY_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
+
+ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mMSE.eps",res=300,width = 12,height = 12)
+ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mVc.eps",res=300,width = 12,height = 12)
 ```

### 2023-02-11 Non_Identical_r0/Rmarkdown/Summary/Best_Subsampling_Method.Rmd
updated plots after adding MSE for MLE in rmarkdown files

---
params:
  Model_Path:
title: "Best Sub-sampling Method: `r params$Model_Path`"
author: "M.Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 12,fig.height = 12,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)
```

```{r load Data}
Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

# Random Sampling
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_RS.RData"))

for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Bias<-All_Bias 
RS_EMSE<-All_EMSE
RS_Info<-All_Info
RS_MSE<-All_MSE
RS_MSE_MLE<-All_MSE_MLE
RS_VAR<-All_VAR
RS_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# OSMAC Model Free
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_MF.RData"))

Accuracy_Data<-cbind(Accuracy_Data[,1],Model="Real Model",Accuracy_Data[,-1])

All_Bias<-All_Bias[All_Bias$Model==Old_Labels[1],]
All_EMSE<-All_EMSE[All_EMSE$Model==Old_Labels[1],]
All_Info<-All_Info[All_Info$Model==Old_Labels[1],]
All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]
Accuracy_Data<-Accuracy_Data[Accuracy_Data$Model==Old_Labels[1],]

## mMSE
All_Bias$Model[All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_EMSE$Model[All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_Info$Model[All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
Accuracy_Data$Model[Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE MF")

OSMAC_MF_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_MF_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_MF_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_MF_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

## mVc
All_Bias$Model[All_Bias$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_EMSE$Model[All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_Info$Model[All_Info$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")
Accuracy_Data$Model[Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc MF")

OSMAC_MF_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_MF_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_MF_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_MF_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")],
                OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")],
                OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
                OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
                OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")],
                OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")],
                OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
                OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")],
                OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
All_ACC<-rbind(RS_ACC,
                OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
                OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")],
                OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])

# Special mMSE elements
SP_All_mMSE_Bias<-rbind(OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                        OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")])
SP_All_mMSE_EMSE<-rbind(OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                        OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")])
SP_All_mMSE_MSE<-rbind(OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                       OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")])
SP_All_mMSE_Info<-rbind(OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                        OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")])
SP_All_mMSE_VAR<-rbind(OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                       OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")])
SP_All_mMSE_ACC<-rbind(OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
                       OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")])

# Special mVc elements
SP_All_mVc_Bias<-rbind(OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                        OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
SP_All_mVc_EMSE<-rbind(OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                        OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
SP_All_mVc_MSE<-rbind(OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
                       OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
SP_All_mVc_Info<-rbind(OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                        OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
SP_All_mVc_VAR<-rbind(OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
                       OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
SP_All_mVc_ACC<-rbind(OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
                       OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove(list = All_Objects[startsWith(All_Objects,"RS")])
```

# Best Sub-sampling Method : `r params$Model_Path`

# Compare SMSE, EMSE, Variance, Information and Bias for all methods.

```{r Compare All,fig.width=20,fig.height=12}
All_Bias %>% 
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

All_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

All_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

All_VAR %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

All_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

All_ACC %>%
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Accuracy")+ggtitle("Accuracy")->p6

ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
```

# Special Comparison of SMSE, EMSE, Variance, Information and Bias for mMSE.
## (Real Model and Assumed Model results with Full Data Real Model)

```{r Special Compare 1,fig.width=20,fig.height=12}
SP_All_mMSE_Bias %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

SP_All_mMSE_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

SP_All_mMSE_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

SP_All_mMSE_VAR %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

SP_All_mMSE_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

SP_All_mMSE_ACC %>%
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Accuracy")+ggtitle("Accuracy")->p6

ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
```

# Compare  SMSE, EMSE, Variance, Information and Bias for mVc.
## (Real Model and Assumed Model results with Full Data Real Model)

```{r Special Compare 2,fig.width=20,fig.height=12}
SP_All_mVc_Bias %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Bias,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Bias")+ggtitle("Bias")->p1

SP_All_mVc_MSE %>%
  ggplot(.,aes(x=Subsample_Size,y=MSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("MSE")+ggtitle("MSE")->p2

SP_All_mVc_EMSE %>%
  ggplot(.,aes(x=Subsample_Size,y=EMSE,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("EMSE")+ggtitle("EMSE")->p3

SP_All_mVc_VAR %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Variance,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Variance")+ggtitle("Variance")->p4

SP_All_mVc_Info %>%
  ggplot(.,aes(x=Subsample_Size,y=mean_Info,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Information")+ggtitle("Information")->p5

SP_All_mVc_ACC %>%
  ggplot(.,aes(x=Subsample_Size,y=Average_Accuracy,color=Model))+
  geom_point()+geom_line()+scale_colour_viridis_d()+
  theme_light()+xlab("Sub sample size")+
  ylab("Average Accuracy")+ggtitle("Accuracy")->p6

ggarrange(p1,p2,p3,p4,p5,p6,common.legend = TRUE,nrow = 2,ncol = 3)
```

### 2023-02-11 Non_Identical_r0/Rmarkdown/Summary/r1_Best_Subsampling_Method.Rmd
updated plots after adding MSE for MLE in rmarkdown files

--- 2023-02-11 Non_Identical_r0/Rmarkdown/Summary/Best_Subsampling_Method.Rmd
@@
 load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC.RData"))
+          "No_Correlated_Covariate_OSMAC_r1.RData"))
 
@@
 load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC_MF.RData"))
+          "No_Correlated_Covariate_OSMAC_MF_r1.RData"))
 

### 2023-02-11 Publication_Ready.Rmd
updated plots after adding MSE for MLE in rmarkdown files

---
params:
  Model_Path:
title: "Publication Ready"
author: "Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 15,fig.height = 20,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)
```

# Using Normal Distribution for Data

## Model : `r params$Model_Path`

```{r load Identical Data}
Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

# Random Sampling
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_RS.RData"))

for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Bias<-All_Bias 
RS_EMSE<-All_EMSE
RS_Info<-All_Info
RS_MSE<-All_MSE
RS_MSE_MLE<-All_MSE_MLE
RS_VAR<-All_VAR
RS_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# OSMAC
load(here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))

All_Bias<-All_Bias[!(All_Bias$Model %in% remove_stuff),]
All_EMSE<-All_EMSE[!(All_EMSE$Model %in% remove_stuff),]
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("RM",paste0("AM ",1:3),"MF")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
               OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
               OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
All_MSE_MLE<-rbind(RS_MSE_MLE,
                   OSMAC_mMSE_MSE_MLE[,!(colnames(OSMAC_mMSE_MSE_MLE) %in% "Type")],
                   OSMAC_mVc_MSE_MLE[,!(colnames(OSMAC_mVc_MSE_MLE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])
All_ACC<-rbind(RS_ACC,
                OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Bias)[3]<-"Estimated Values"
colnames(All_EMSE)[3]<-"Estimated Values"
colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_VAR)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

Final_Data_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
                               cbind.data.frame(Metric="EMSE",All_EMSE),
                               cbind.data.frame(Metric="Model Information",All_Info),
                               cbind.data.frame(Metric="MSE",All_MSE),
                               cbind.data.frame(Metric="MSE_MLE",All_MSE_MLE),
                               cbind.data.frame(Metric="Variance",All_VAR),
                               cbind.data.frame(Metric="Accuracy",All_ACC))

remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR,All_ACC)
```

```{r load Non Identical Data}
Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
New_Labels<-c("RM",paste0("AM ",1:3))

# OSMAC
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC.RData"))

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_VAR$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR)

# OSMAC Model Free
load(here("Non_Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
          "No_Correlated_Covariate_OSMAC_MF.RData"))

Accuracy_Data<-cbind(Model="Real Model",Accuracy_Data)

Old_Labels[1]<-c("Real Model")

All_Bias<-All_Bias[All_Bias$Model==Old_Labels[1],]
All_EMSE<-All_EMSE[All_EMSE$Model==Old_Labels[1],]
All_Info<-All_Info[All_Info$Model==Old_Labels[1],]
All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
All_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Model==Old_Labels[1],]
All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]
Accuracy_Data<-Accuracy_Data[Accuracy_Data$Model==Old_Labels[1],]

## mMSE
All_Bias$Model[All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_EMSE$Model[All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_Info$Model[All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_MSE_MLE$Model[All_MSE_MLE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
Accuracy_Data$Model[Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE MF")

OSMAC_MF_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_MF_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_MF_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_MF_mMSE_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mMSE",]
OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_MF_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

## mVc
All_Bias$Model[All_Bias$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_EMSE$Model[All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_Info$Model[All_Info$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_MSE_MLE$Model[All_MSE_MLE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")
Accuracy_Data$Model[Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc MF")

OSMAC_MF_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_MF_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_MF_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_MF_mVc_MSE_MLE<-All_MSE_MLE[All_MSE_MLE$Type == "mVc",]
OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_MF_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")],
                OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")],
                OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
               OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
               OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
               OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")],
               OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
All_MSE_MLE<-rbind(RS_MSE_MLE,
                   OSMAC_mMSE_MSE_MLE[,!(colnames(OSMAC_mMSE_MSE_MLE) %in% "Type")],
                   OSMAC_mVc_MSE_MLE[,!(colnames(OSMAC_mVc_MSE_MLE) %in% "Type")],
                   OSMAC_MF_mMSE_MSE_MLE[,!(colnames(OSMAC_MF_mMSE_MSE_MLE) %in% "Type")],
                   OSMAC_MF_mVc_MSE_MLE[,!(colnames(OSMAC_MF_mVc_MSE_MLE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")],
                OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
               OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
               OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
               OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")],
               OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
All_ACC<-rbind(RS_ACC,
               OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
               OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
               OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")],
               OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])
remove(list = All_Objects[startsWith(All_Objects,"RS")])

All_Bias$Model<-factor(All_Bias$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                               "OSMAC mMSE RM","OSMAC mVc RM",
                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                               "OSMAC mMSE MF","OSMAC mVc MF"))
All_EMSE$Model<-factor(All_EMSE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                               "OSMAC mMSE RM","OSMAC mVc RM",
                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                               "OSMAC mMSE MF","OSMAC mVc MF"))
All_Info$Model<-factor(All_Info$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                               "OSMAC mMSE RM","OSMAC mVc RM",
                                               "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                               "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                               "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                               "OSMAC mMSE MF","OSMAC mVc MF"))
All_MSE$Model<-factor(All_MSE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                             "OSMAC mMSE RM","OSMAC mVc RM",
                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                             "OSMAC mMSE MF","OSMAC mVc MF"))
All_MSE_MLE$Model<-factor(All_MSE_MLE$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                                     "OSMAC mMSE RM","OSMAC mVc RM",
                                                     "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                                     "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                                     "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                                     "OSMAC mMSE MF","OSMAC mVc MF"))
All_VAR$Model<-factor(All_VAR$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                             "OSMAC mMSE RM","OSMAC mVc RM",
                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                             "OSMAC mMSE MF","OSMAC mVc MF"))
All_ACC$Model<-factor(All_ACC$Model,levels=c("RS RM","RS AM 1","RS AM 2","RS AM 3",
                                             "OSMAC mMSE RM","OSMAC mVc RM",
                                             "OSMAC mMSE AM 1","OSMAC mVc AM 1",
                                             "OSMAC mMSE AM 2","OSMAC mVc AM 2",
                                             "OSMAC mMSE AM 3","OSMAC mVc AM 3",
                                             "OSMAC mMSE MF","OSMAC mVc MF"))

colnames(All_Bias)[3]<-"Estimated Values"
colnames(All_EMSE)[3]<-"Estimated Values"
colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_VAR)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

Final_Data_Non_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
                                   cbind.data.frame(Metric="EMSE",All_EMSE),
                                   cbind.data.frame(Metric="Model Information",All_Info),
                                   cbind.data.frame(Metric="MSE",All_MSE),
                                   cbind.data.frame(Metric="MSE_MLE",All_MSE_MLE),
                                   cbind.data.frame(Metric="Variance",All_VAR),
                                   cbind.data.frame(Metric="MSE Y",All_ACC))

remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR)
```

```{r Identical r0 Plots}
# mMSE models Colors
Selected_mMSE<-c(#"RS RM",
                 #"RS AM 1","RS AM 2","RS AM 3",
                 "OSMAC mMSE RM",
                 "OSMAC mMSE AM 1","OSMAC mMSE AM 2","OSMAC mMSE AM 3",
                 "OSMAC mMSE MF")
Colors_mMSE<-c(#"#88CCEE",
               #"#A6C3D3","#5D92B0","#35586C", 
               "#FFC4D8", 
               "#E28490","#BB2C3E","#55141C", 
               "#DDCC77")
# mvc models
Selected_mVc<-c(#"RS RM",
                #"RS AM 1","RS AM 2","RS AM 3",
                "OSMAC mVc RM",
                "OSMAC mVc AM 1","OSMAC mVc AM 2","OSMAC mVc AM 3",
                "OSMAC mVc MF")
Colors_mVc<-c(#"#88CCEE",
              #"#A6C3D3","#5D92B0","#35586C", 
              "#FFC4D8", 
               "#E28490","#BB2C3E","#55141C", 
               "#DDCC77")

Final_Data<-rbind(cbind(Data="Identical r0",Final_Data_Identical_r0),
                  cbind(Data="Non Identical r0",Final_Data_Non_Identical_r0))

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p1

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p2

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p3

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p4

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p5

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p6

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p7

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p8

ggarrange(p1,p2,p3,p4,nrow = 4)
ggarrange(p5,p6,nrow = 2)
ggarrange(p7,p8,nrow = 2)
```

```{r Identical r0 Plots with gg.gap,fig.height=4}
SS_Choice<-100*c(10:15)

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p1_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p2_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p3_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p4_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p5_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p6_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p7_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p8_New

```

```{r All Plots}
ggarrange(p1,p1_New,
          p2,p2_New,nrow = 4)

ggarrange(p5_New,p6_New,nrow = 2)
ggarrange(p7_New,p8_New,nrow = 2)
```

### 2023-02-11 r1_Articles.Rmd
updated plots after adding MSE for MLE in rmarkdown files

---
title: "Articles_Plots"
author: "Amalan"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width = 14,fig.height = 16,message = FALSE,warning = FALSE)
library(here)
library(ggplot2)
library(dplyr)
library(tidyr)
library(LaplacesDemon)
library(xtable)
library(flextable)
library(grid)
library(cowplot)
library(linguisticsdown)
library(ggpubr)

```

# Using Normal Distribution for Data

```{r Load data model 1}
Model_1_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Average MSE Y",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)

```

```{r Load data model 2}
Model_2_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & Accuracy_Data$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M2_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)

```

```{r Load data model 3}
Model_3_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,All_ACC)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M3_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",Metric="Average MSE Y",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE)

```

```{r Load data model 4}
Model_4_SS<-1000

# OSMAC
load(here("Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
New_Labels<-c("DM",paste0("AM ",1:3),"MR")

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mMSE"] <-paste0("mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Info$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_MSE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_MSE_MLE$Model[All_MSE_MLE$Model==Old_Labels[i] & All_MSE_MLE$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
  All_ACC$Model[All_ACC$Model==Old_Labels[i] & All_ACC$Type == "mVc"] <-paste0("mVc ",New_Labels[i])
}

OSMAC_Info<-All_Info
OSMAC_MSE<-All_MSE
OSMAC_MSE_MLE<-All_MSE_MLE
OSMAC_ACC<-All_ACC

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,All_ACC)

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M4_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Model Information",All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE",All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="MSE for MLE",All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2",
                                        Metric="Average MSE Y",All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,RS_ACC)

```

```{r combine data and plot,fig.width = 8,fig.height = 12}
Identical_ro<-rbind(M1_Identical_r0,M2_Identical_r0,
                    M3_Identical_r0,M4_Identical_r0)

Identical_ro$Covariate<-factor(Identical_ro$Covariate,
                               levels = c("Data Model: x\u2081, x\u2082",
                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2",
                                          "Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",
                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"))

Identical_ro$Model<-factor(Identical_ro$Model,
                           levels = c("mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
                                      "mMSE MR","mVc MR"))

Identical_ro$Model<-recode_factor(Identical_ro$Model,
                                  `mMSE DM`="Optimal subsampling mMSE: Data Model",
                                  `mMSE AM 1`="Optimal subsampling mMSE: Incorrect Model 1",
                                  `mMSE AM 2`="Optimal subsampling mMSE: Incorrect Model 2",
                                  `mMSE AM 3`="Optimal subsampling mMSE: Incorrect Model 3",
                                  `mVc DM`="Optimal subsampling mVc: Data Model",
                                  `mVc AM 1`="Optimal subsampling mVc: Incorrect Model 1",
                                  `mVc AM 2`="Optimal subsampling mVc: Incorrect Model 2",
                                  `mVc AM 3`="Optimal subsampling mVc: Incorrect Model 3",
                                  `mMSE MR`="Model Robust subsampling mMSE: Data Model",
                                  `mVc MR`="Model Robust subsampling mVc: Data Model")

Selected_Models_mMSE<-c("Optimal subsampling mMSE: Data Model",
                        "Optimal subsampling mMSE: Incorrect Model 1",
                        "Optimal subsampling mMSE: Incorrect Model 2",
                        "Optimal subsampling mMSE: Incorrect Model 3",
                        "Model Robust subsampling mMSE: Data Model")

# Colors_mMSE<-c("#FFC4D8","#E28490","#BB2C3E","#55141C",
#                "#DDCC77")

Colors_mMSE<-c("#cc0000", 
               "#ff578a","#ff578a","#ff578a",
               "darkgreen")

Selected_Models_mVc<-c("Optimal subsampling mVc: Data Model",
                       "Optimal subsampling mVc: Incorrect Model 1",
                       "Optimal subsampling mVc: Incorrect Model 2",
                       "Optimal subsampling mVc: Incorrect Model 3",
                       "Model Robust subsampling mVc: Data Model")

# Colors_mVc<-Colors_mVc<-c("#FFC4D8","#E28490","#BB2C3E","#55141C", 
#                           "#DDCC77")

Colors_mVc<-c("#cc0000", 
              "#ff578a","#ff578a","#ff578a",
              "darkgreen")

Theme_special<-function()
{
  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
        axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
        strip.text = element_text(colour = "black",size = 12,face="bold"),
        panel.grid.minor.x = element_blank(),
        axis.title= element_text(color = "black",face = "bold",size = 12),
        legend.text = element_text(color = "black", size=11),
        legend.position = "bottom",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-1,-2,-1,-2)) 
}

#Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE

Temp_legend_mMSE<-get_legend(Temp_plot_mMSE)

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc

Temp_legend_mVc<-get_legend(Temp_plot_mVc)

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p4

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p5

Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p6

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p7

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+#expand_limits(y = 0)+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p8

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto")
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto")
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")
ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggsave(filename = "r1_SMSE_MI_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggsave(filename = "r1_SMSE_MI_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 12)

ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mMSE.eps",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mVc.eps",res=300,width = 12,height = 12)
```

### 2023-02-11 r1_Publication_Ready.Rmd
updated plots after adding MSE for MLE in rmarkdown files

--- 2023-02-11 Publication_Ready.Rmd
@@
 load(here("Identical_r0","Summary",params$Model_Path,"Data","Efficiency",
-          "No_Correlated_Covariate_OSMAC.RData"))
+          "No_Correlated_Covariate_OSMAC_r1.RData"))
 remove_stuff<-c(paste0("Assumed New ",1:3))
@@
 ```
-
-```{r Identical r0 Plots with gg.gap,fig.height=4}
-SS_Choice<-100*c(10:15)
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p1_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p2_New
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Model Information") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p3_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p4_New
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE Y") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p5_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE Y") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Average MSE Y",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p6_New
-
-Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "MSE_MLE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mMSE")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p7_New
-
-Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "MSE_MLE") & 
-             Final_Data$Subsample_Size %in% SS_Choice,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
-  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
-  theme_light()+xlab("Sub sample size")+
-  ggtitle("Comparing Simulated MSE for MLE",subtitle = "mVc")+
-  ylab("Estimated Values")+facet_wrap(~Data)->p8_New
-
-```
-
-```{r All Plots}
-ggarrange(p1,p1_New,
-          p2,p2_New,nrow = 4)
-
-ggarrange(p5_New,p6_New,nrow = 2)
-ggarrange(p7_New,p8_New,nrow = 2)
-```

### 2023-02-11 Identical_r0/Rmarkdown/Summary/Summary_Rmarkdown.R

@@ -1,5 +1,4 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
@@ -8,11 +7,16 @@ Model<-c("Model_1","Model_2",
 # Best_Subsampling_Method ----
 for (i in 1:length(Model))
 {
-ezknit(file=here("Identical_r0","Rmarkdown","Classical","Summary","Best_Subsampling_Method.Rmd"),
-        out_dir=here("Identical_r0","Summary","Classical",Model[i],"Best_Subsampling"),
-        fig_dir = c("Plots"),
-        params=list("Model_Path"=Model[i]),
-        verbose = TRUE,keep_md = FALSE)
-#open_output_dir()
+  # render(input=here("Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "Best_Subsampling_Method",
+  #        output_dir=here("Identical_r0","Summary",Model[i],"Best_Subsampling"),
+  #        params=list("Model_Path"=Model[i]))
+  
+  render(input=here("Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "r1_Best_Subsampling_Method",
+         output_dir=here("Identical_r0","Summary",Model[i],"Best_Subsampling"),
+         params=list("Model_Path"=Model[i]))
 }
 

### 2023-02-11 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -20,8 +20,8 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
     PI.prop <- rep(1/n, n)
     idx.prop <- sample(1:n, r1, T, PI.prop)
     
-    x.prop<-lapply(1:length(combs),function(j){
-      X[idx.prop,All_Covariates %in% combs[[j]]] # Assumed Data 
+    x.prop<-lapply(1:length(combs),function(a){
+      X[idx.prop,All_Covariates %in% combs[[a]]] # Assumed Data 
     })
     y.prop <- Y[idx.prop,]  # Assumed Data 
     
@@ -30,16 +30,16 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
     
     pinv.prop <- rep(n,r1)
     
-    fit.prop <- lapply(1:length(combs), function(j){
-      glm(y.prop~x.prop[[j]]-1,family = "poisson")# Assumed Data
+    fit.prop <- lapply(1:length(combs), function(a){
+      glm(y.prop~x.prop[[a]]-1,family = "poisson")# Assumed Data
     })
     fit_Real.prop <- glm(y_Real.prop~x_Real.prop-1,family = "poisson") # Real Data
     
     beta.prop<-list()
-    for (j in 1:length(combs)) 
+    for (a in 1:length(combs)) 
       {
-      beta.prop[[j]] <- fit.prop[[j]]$coefficients # Assumed Data
-      if(anyNA(beta.prop[[j]]))
+      beta.prop[[a]] <- fit.prop[[a]]$coefficients # Assumed Data
+      if(anyNA(beta.prop[[a]]))
         {
         return(list(opt=NA, msg="first stage not converge"))
         }
@@ -49,8 +49,8 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
     if(anyNA(beta_Real.prop[1]))
       return(list(opt=NA, msg="first stage not converge"))
     
-    P.prop  <- lapply(1:length(combs),function(j){
-      exp(X[,All_Covariates %in% combs[[j]] ] %*% beta.prop[[j]]) # Assumed Data
[…]

### 2023-02-11 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R

@@ -3,7 +3,7 @@ library(compiler)
 library(LaplacesDemon)
 
 # Load the OSMAC algorithm
-source(here("Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Algorithm.R"))
+source(here("Identical_r0","Simulation_Setup","R_Scripts","OSMAC_Algorithm.R"))
 
 AlgTwoStp<-cmpfun(AlgTwoStp)
 Cordeiro<-cmpfun(Cordeiro)
@@ -182,12 +182,12 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
   
   save(list= c("Results_OSMAC","Bias_OSMAC","Utility_OSMAC"#,"Sample_OSMAC","Probability"
                ),
-       file = here("Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC",
+       file = here("Identical_r0","Simulation_Setup","Analysis","OSMAC",
                    "Results","Real_Model","OSMAC_output.RData"))
   
   save(list = c("Results_OSMAC","Bias_OSMAC","Utility_OSMAC"#,"Sample_OSMAC","Probability"
                 ),
-       file = here("Identical_r0","Outputs","Classical",Model_Path,"OSMAC","Real_Model","OSMAC_output.RData"))
+       file = here("Identical_r0","Outputs",Model_Path,"OSMAC","Real_Model","OSMAC_output.RData"))
   
   # Assumed Model Old
   for (j in 1:length(combs)) 
@@ -232,12 +232,12 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
     
     save(list= c("Results_OSMAC","Bias_OSMAC","Utility_OSMAC"#,"Sample_OSMAC","Probability"
                  ),
-         file = here("Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC",
+         file = here("Identical_r0","Simulation_Setup","Analysis","OSMAC",
                      "Results","Assumed_Model",paste0("OSMAC_output_Old_",j,".RData")))
     
     save(list = c("Results_OSMAC","Bias_OSMAC","Utility_OSMAC"#,"Sample_OSMAC","Probability"
                   ),
-         file = here("Identical_r0","Outputs","Classical",Model_Path,"OSMAC",
[…]

### 2023-02-11 Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Algorithm.R

@@ -1,0 +1,533 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two step OSMAC ----
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
+  Y_Real<-Real_Data[,1] #  Real Data
+  X_Real<-Real_Data[,-1] # Real Data
+  
+  PI.prop <- rep(1/n, n)
+  
+  # For the Real Model 
+  beta.mVc_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  Utility_mVc_Real<-matrix(nrow = length(r1),ncol = 3 )
+  Bias_mVc_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  
+  beta.mMSE_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  Utility_mMSE_Real<-matrix(nrow = length(r1),ncol = 3 )
+  Bias_mMSE_Real<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+  
+  #Sample.mMSE_Real<-list()
+  #Sample.mVc_Real<-list()
+  
+  beta.mVc_Old<-Utility_mVc_Old<-Bias_mVc_Old<-list()
+  beta.mMSE_Old<-Utility_mMSE_Old<-Bias_mMSE_Old<-list()
+  #Sample.mMSE_Assumed_Old<-list()
+  #Sample.mVc_Assumed_Old<-list()
+  
+  # For the Assumed Model with Already Available Sub-sampling probabilities
+  for (a in 1:length(combs)) 
+  {
+    beta.mVc_Old[[a]]<-matrix(nrow = length(r1),ncol = ncol(X_Real) )
+    Utility_mVc_Old[[a]]<-matrix(nrow = length(r1),ncol = 3 )
[…]

### 2023-02-11 Non_Identical_r0/Rmarkdown/Random_Sampling_And_OSMAC.R

@@ -1,34 +1,42 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
-         "Model_3","Model_4") ; j=4
+         "Model_3","Model_4") ; j=1
 
-# Random Sampling ----
 for (j in 1:length(Model)) 
 {
-  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","Random_Sampling.Rmd"),
-         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"Random_Sampling"),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[j]),
-         verbose = TRUE,keep_md = FALSE)
-  #open_output_dir()
+  # Random Sampling ----
+  render(input = here("Non_Identical_r0","Rmarkdown","Random_Sampling.Rmd"),
+         output_format = "html_document",
+         output_file = "Random_Sampling",
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"Random_Sampling"),
+         params = list("Model_Path"=Model[j]))
   
   # OSMAC Method ----
-  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Method.Rmd"),
-         out_dir=here("Non_Identical_r0","htmloutputs","Classical",Model[j],"OSMAC"),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[j]),
-         verbose = TRUE,keep_md = FALSE)
-  #open_output_dir()
+  render(input = here("Non_Identical_r0","Rmarkdown","OSMAC_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "OSMAC_Method",
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
+         params = list("Model_Path"=Model[j]))
+  
+  render(input = here("Non_Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
+         output_format = "html_document",
+         output_file = "r1_OSMAC_Method",
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
+         params = list("Model_Path"=Model[j]))
   
   # OSMAC Model Free Method ----
-  ezknit(file=here("Non_Identical_r0","Rmarkdown","Classical","OSMAC_Model_Free_Method.Rmd"),
[…]

### 2023-02-11 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC/Simulation_Results_OSMAC_Sampling.R

@@ -6,10 +6,10 @@ library(LaplacesDemon)
 enableJIT(1)
 
 # Load the No Correlated Data----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Init.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","Init.RData"))
 
 # Load the OSMAC Sample----
-load(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Run_OSMAC.RData"))
+load(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","Run_OSMAC.RData"))
 
 # Real Model ----
 # Generate for Random sample of 1000 different times ---

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -38,12 +38,20 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
     #Sample.mMSE<-list()
     #Sample.mVc<-list()
     
-    ## mVC
+    ## mVc
+    PI.mVc <- sqrt((Y - P.prop)^2 * rowSums(X^2))
+    PI.mVc <- PI.mVc / sum(PI.mVc)
+    
+    ## mMSE
+    p.prop <- P.prop[idx.prop]
+    w.prop <- p.prop
+    W.prop <- solve(t(x.prop) %*% (x.prop * w.prop * pinv.prop))
+    PI.mMSE <- sqrt((Y - P.prop)^2 * rowSums((X%*%W.prop)^2))
+    PI.mMSE <- PI.mMSE / sum(PI.mMSE)
+    
     for (i in 1:length(r2)) 
     {
-      PI.mVc <- sqrt((Y - P.prop)^2 * rowSums(X^2))
-      PI.mVc <- PI.mVc / sum(PI.mVc)
-      
+      # mVc
       idx.mVc <- sample(1:n, r2[i]-r1, T, PI.mVc)
       x.mVc <- X[c(idx.mVc, idx.prop),]
       y.mVc <- Y[c(idx.mVc, idx.prop)]
@@ -65,11 +73,6 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       Bias_mVc[i,]<-Cordeiro(XData=x.mVc,With_bias = beta.mVc[i,])
       
       ## mMSE
-      p.prop <- P.prop[idx.prop]
-      w.prop <- p.prop
-      W.prop <- solve(t(x.prop) %*% (x.prop * w.prop * pinv.prop))
-      PI.mMSE <- sqrt((Y - P.prop)^2 * rowSums((X%*%W.prop)^2))
-      PI.mMSE <- PI.mMSE / sum(PI.mMSE)
       idx.mMSE <- sample(1:n, r2[i]-r1, T, PI.mMSE)
       x.mMSE <- X[c(idx.mMSE, idx.prop),]
       y.mMSE <- Y[c(idx.mMSE, idx.prop)]
@@ -130,12 +133,20 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
     #Sample.mMSE<-list()
     #Sample.mVc<-list()
     
[…]

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/OSMAC_Algorithm_Model_Free.R

@@ -13,29 +13,27 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two Step OSMAC ----
-OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) {
-  
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) 
+{
   PI.prop <- rep(1/n, n)
   idx.prop <- sample(1:n, r1, T, PI.prop)
   
   y.prop <- Y[idx.prop]
   pinv.prop <- rep(n,r1)
   
-  beta.prop<-list()
-  beta.prop<-lapply(1:length(combs),function(i) {
-    glm(y.prop~X[idx.prop,colnames(X) %in% combs[[i]]]-1, family = "poisson")})
+  beta.prop<-lapply(1:length(combs),function(a) {
+    glm(y.prop~X[idx.prop,colnames(X) %in% combs[[a]]]-1, family = "poisson")})
    
-  for (i in 1:length(combs)) 
+  for (j in 1:length(combs)) 
   {
-    if (anyNA(beta.prop[[i]]$coefficients))
+    if (anyNA(beta.prop[[j]]$coefficients))
     {
       stop("There are NA or NaN values")
     }
   }
   
-  P.prop<-list()
-  P.prop<-lapply(1:length(combs), function(i)
-    exp(X[,colnames(X) %in% combs[[i]]] %*% beta.prop[[i]]$coefficients))
+  P.prop<-lapply(1:length(combs), function(a)
+    exp(X[,colnames(X) %in% combs[[a]]] %*% beta.prop[[a]]$coefficients))
   
   beta.mVc<-Utility_mVc<-Bias_mVc<-list()
   beta.mMSE<-Utility_mMSE<-Bias_mMSE<-list()
@@ -54,22 +52,36 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) {
   #Sample.mMSE<-list()
   #Sample.mVc<-list()
   
+  ## mVc
+  PI.mVc<-lapply(1:length(combs),function(a){
+    PI.mVc <- sqrt((Y - P.prop[[a]])^2 * rowSums(X[,All_Covariates %in% combs[[a]] ]^2)) #
+    return(PI.mVc / sum(PI.mVc))})
+  
[…]

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/OSMAC_Model_Free_Setup.R

@@ -4,7 +4,7 @@ library(LaplacesDemon)
 library(matrixStats)
 
 # Load the OSMAC algorithm
-source(here("Non_Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Model_Free",
+source(here("Non_Identical_r0","Simulation_Setup","R_Scripts","OSMAC_Model_Free",
             "OSMAC_Algorithm_Model_Free.R"))
 
 OSMAC_MF<-cmpfun(OSMAC_MF)
@@ -102,22 +102,22 @@ Run_OSMAC_MF<-function(Replicates,r1,r2,Y,X,alpha,combs,All_Covariates,N)
   
   save(list= c(paste0("Results_OSMAC_",1:length(combs)),paste0("Bias_OSMAC_",1:length(combs)),
                paste0("Utility_OSMAC_",1:length(combs))),
-       file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC_Model_Free",
+       file = here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC_Model_Free",
                    "Results","OSMAC_MF_output.RData"))
 
   save(list = c(paste0("Results_OSMAC_",1:length(combs)),paste0("Bias_OSMAC_",1:length(combs)),
                 paste0("Utility_OSMAC_",1:length(combs))),
-       file = here("Non_Identical_r0","Outputs","Classical",Model_Path,"OSMAC_Model_Free",
+       file = here("Non_Identical_r0","Outputs",Model_Path,"OSMAC_Model_Free",
                    "OSMAC_MF_output.RData"))
   
   # for (i in 1:length(combs)) 
   # {
   #   save(list = c(paste0("Sample_OSMAC_",i)),
-  #        file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC_Model_Free",
+  #        file = here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC_Model_Free",
   #                    "Results",paste0("OSMAC_MF_Samples_output_",i,".RData")))
   #   
   #   save(list = c(paste0("Sample_OSMAC_",i)),
-  #        file = here("Non_Identical_r0","Outputs","Classical",Model_Path,"OSMAC_Model_Free",
+  #        file = here("Non_Identical_r0","Outputs",Model_Path,"OSMAC_Model_Free",
[…]

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/r1_OSMAC_Algorithm_Model_Free.R

@@ -1,0 +1,180 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two Step OSMAC ----
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) 
+{
+  PI.prop <- rep(1/n, n)
+  
+  beta.mVc<-Utility_mVc<-Bias_mVc<-list()
+  beta.mMSE<-Utility_mMSE<-Bias_mMSE<-list()
+  
+  for (a in 1:length(combs)) 
+  {
+    beta.mVc[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]])) #
+    Utility_mVc[[a]]<-matrix(nrow = length(r1),ncol = 3 ) #
+    Bias_mVc[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]])) #
+    
+    beta.mMSE[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]])) #
+    Utility_mMSE[[a]]<-matrix(nrow = length(r1),ncol = 3) #
+    Bias_mMSE[[a]]<-matrix(nrow = length(r1),ncol = length(combs[[a]]))  #
+  }
+  
+  #Sample.mMSE<-list()
+  #Sample.mVc<-list()
+  
+  for (i in 1:length(r1)) 
+  {
+    idx.prop <- sample(1:n, r1[i], T, PI.prop)
+    
+    y.prop <- Y[idx.prop]
+    pinv.prop <- rep(n,r1[i])
+    
+    beta.prop<-lapply(1:length(combs),function(a) {
+      glm(y.prop~X[idx.prop,colnames(X) %in% combs[[a]]]-1, family = "poisson")})
+    
+    for (j in 1:length(combs)) 
+    {
+      if (anyNA(beta.prop[[j]]$coefficients))
+      {
+        stop("There are NA or NaN values")
[…]

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R

@@ -3,7 +3,7 @@ library(compiler)
 library(LaplacesDemon)
 
 # Load the OSMAC algorithm
-source(here("Non_Identical_r0","Simulation_Setup","Classical","R_Scripts","OSMAC_Algorithm.R"))
+source(here("Non_Identical_r0","Simulation_Setup","R_Scripts","OSMAC_Algorithm.R"))
 
 AlgTwoStp<-cmpfun(AlgTwoStp)
 Cordeiro<-cmpfun(Cordeiro)
@@ -82,21 +82,21 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,Model)
   
   save(list= c("Results_OSMAC","Bias_OSMAC","Utility_OSMAC"#,"Sample_OSMAC"
                ),
-       file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Results",Model,"OSMAC_output.RData"))
+       file = here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","Results",Model,"OSMAC_output.RData"))
 
   save(list = c("Results_OSMAC","Bias_OSMAC","Utility_OSMAC"#,"Sample_OSMAC"
                 ),
-       file = here("Non_Identical_r0","Outputs","Classical",Model_Path,"OSMAC",Model,"OSMAC_output.RData"))
+       file = here("Non_Identical_r0","Outputs",Model_Path,"OSMAC",Model,"OSMAC_output.RData"))
 }
 
 Run_OSMAC<-cmpfun(Run_OSMAC)
 
 #Save the OSMAC Sample function----
 save(list =c("Run_OSMAC","AlgTwoStp","Cordeiro"),
-     file=here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC","Run_OSMAC.RData"))
+     file=here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC","Run_OSMAC.RData"))
 
 rm(list = ls())
 
 # Run the OSMAC sampling method ----
-source(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","OSMAC",
+source(here("Non_Identical_r0","Simulation_Setup","Analysis","OSMAC",
             "Simulation_Results_OSMAC_Sampling.R"))

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/Random_Sampling_Setup.R

@@ -76,10 +76,10 @@ Run_RandomSample<-cmpfun(Run_RandomSample)
 
 #Save the Random Sample function for No Correlated Covariate Data ----
 save(Run_RandomSample,Cordeiro,
-     file=here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling","Run_RandomSample.RData"))
+     file=here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling","Run_RandomSample.RData"))
 
 rm(list = ls())
 
 # Run the Random sampling method ----
-source(here("Non_Identical_r0","Simulation_Setup","Classical","Analysis","Random_Sampling",
+source(here("Non_Identical_r0","Simulation_Setup","Analysis","Random_Sampling",
             "Simulation_Results_Random_Sampling.R"))

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/Setup_Data.R

@@ -1,9 +1,9 @@
 library(here)
 
-Model_Path<-"Model_1"
+#Model_Path<-"Model_1"
 #Model_Path<-"Model_2"
 #Model_Path<-"Model_3"
-#Model_Path<-"Model_4"
+Model_Path<-"Model_4"
 
 # Random Sampling Data ----
 Base_Path<-"Random_Sampling"
@@ -11,8 +11,8 @@ Base_Path<-"Random_Sampling"
 ## No Correlated Covariate Data -----
 load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
 save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path"),
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
-                 Base_Path,"Init.RData"))        
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis",
+                 Base_Path,"Init.RData"))
 
 # OSMAC Data ----
 Base_Path<-"OSMAC"
@@ -20,7 +20,7 @@ Base_Path<-"OSMAC"
 ## No Correlated Covariate Data -----
 load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
 save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis",
                  Base_Path,"Init.RData"))        
 
 remove(Base_Path)
@@ -31,7 +31,7 @@ Base_Path<-"OSMAC_Model_Free"
 ## No Correlated Covariate Data -----
 load(here("Non_Identical_r0","Generate_Big_Data",Model_Path,"No_Correlated_Covariate.RData"))
 save(list = c("Simulated_Data","Replicates","Subsample_Size","Model_Path","r0"),
-     file = here("Non_Identical_r0","Simulation_Setup","Classical","Analysis",
+     file = here("Non_Identical_r0","Simulation_Setup","Analysis",
                  Base_Path,"Init.RData"))
 
 remove(Base_Path)

### 2023-02-11 Non_Identical_r0/Simulation_Setup/R_Scripts/r1_OSMAC_Algorithm.R

@@ -1,0 +1,209 @@
+# Cordeiro Bias Estimation ----
+Cordeiro<-function(XData,With_bias)
+{
+  p <- as.vector(exp(XData%*%as.vector(With_bias)))
+  W <- diag(p)
+  inverse_term <- solve(t(XData)%*%W%*%XData)
+  
+  Term1 <- inverse_term%*%t(XData)%*%W
+  Term2 <- diag(diag(XData%*%(inverse_term)%*%t(XData))) %*% rep(-0.5,nrow(XData))
+  
+  bias <- as.vector(Term1%*%Term2)
+  return(bias)
+}
+
+# Two step OSMAC ----
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
+  if(Model=="Real_Model")
+  {
+    PI.prop <- rep(1/n, n)
+    
+    beta.mVc<-matrix(nrow = length(r1),ncol = ncol(X) )
+    Utility_mVc<-matrix(nrow = length(r1),ncol = 3 )
+    Bias_mVc<-matrix(nrow = length(r1),ncol = ncol(X) )
+    
+    beta.mMSE<-matrix(nrow = length(r1),ncol = ncol(X) )
+    Utility_mMSE<-matrix(nrow = length(r1),ncol = 3 )
+    Bias_mMSE<-matrix(nrow = length(r1),ncol = ncol(X) )
+    
+    #Sample.mMSE<-list()
+    #Sample.mVc<-list()
+    
+    for (i in 1:length(r1)) 
+    {
+      idx.prop <- sample(1:n, r1[i], T, PI.prop)
+      x.prop <- X[idx.prop,]
+      y.prop <- Y[idx.prop]
+      pinv.prop <- rep(n,r1[i])
+      fit.prop <- glm(y.prop~x.prop-1,family = "poisson")
+      beta.prop <- fit.prop$coefficients
+      if (is.na(beta.prop[1]))
+        return(list(opt=NA, msg="first stage not converge"))
+      P.prop  <- exp(X %*% beta.prop)
+      
+      ## mVc
+      PI.mVc <- sqrt((Y - P.prop)^2 * rowSums(X^2))
+      PI.mVc <- PI.mVc / sum(PI.mVc)
+      
+      ## mMSE
[…]

### 2023-02-11 Publication_Ready_command.R

@@ -1,5 +1,4 @@
 library(here)
-library(ezknitr)
 library(rmarkdown)
 
 Model<-c("Model_1","Model_2",
@@ -8,10 +7,15 @@ Model<-c("Model_1","Model_2",
 for(i in 1:length(Model))
 {
   # Publication Ready ----
-  ezknit(file=here("Publication_Ready.Rmd"),
-         out_dir=here("Publication_Ready",Model[i]),
-         fig_dir = c("Plots"),
-         params=list("Model_Path"=Model[i]),
-         verbose = TRUE,keep_md = TRUE,keep_html = FALSE)
-  #open_output_dir()
+  # render(input=here("Publication_Ready.Rmd"),
+  #        output_format = "github_document",
+  #        output_file = "Publication_Ready",
+  #        output_dir=here("Publication_Ready",Model[i]),
+  #        params=list("Model_Path"=Model[i]))
+  
+  render(input=here("r1_Publication_Ready.Rmd"),
+         output_format = "github_document",
+         output_file = "r1_Publication_Ready",
+         output_dir=here("Publication_Ready",Model[i]),
+         params=list("Model_Path"=Model[i]))
 }

### 2023-02-12 Articles.Rmd
article plots location changed

@@
 
+LineType_mMSE<-c("twodash", 
+                 "dashed",
+                 "dotted","dotted","dotted",
+                 "solid")
+
 Selected_Models_mVc<-c("Random Sampling: Data Model",
@@
 
+LineType_mVc<-c("twodash", 
+                "dashed",
+                "dotted","dotted","dotted",
+                "solid")
+
 Theme_special<-function()
 {
-  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
+  theme(legend.key.width=unit(1.2,"cm"),
+        axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
         axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  #geom_point(size=1.75)+
+  geom_line(size=1)+
   scale_color_manual(values=Colors_mMSE)+
+  scale_linetype_manual(values=LineType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+  #geom_point(size=1.75)+
+  geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+  
+  scale_linetype_manual(values=LineType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   scale_color_manual(values=Colors_mMSE)+
+  scale_linetype_manual(values=LineType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
   scale_color_manual(values=Colors_mVc)+
+  scale_linetype_manual(values=LineType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
@@
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","ACCURACY_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","ACCURACY_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggsave(filename = "SMSE_MI_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mMSE.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-  ggsave(filename = "SMSE_MI_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mVc.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggsave(filename = "ACCURACY_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","ACCURACY_PR_TV_Nor_mMSE.eps"),device="eps",dpi=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggsave(filename = "ACCURACY_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","ACCURACY_PR_TV_Nor_mVc.eps"),device="eps",dpi=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mMSE.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Nor_mMSE.eps"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "SMSE_for_MLE_MI_PR_TV_Nor_mVc.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","SMSE_for_MLE_MI_PR_TV_Nor_mVc.eps"),res=300,width = 12,height = 12)
 ```

### 2023-02-12 r1_Articles.Rmd
article plots location changed

@@
 
+LineType_mMSE<-c("dashed",
+                 "dotted","dotted","dotted",
+                 "solid")
+
 Selected_Models_mVc<-c("Optimal subsampling mVc: Data Model",
@@
 
+LineType_mVc<-c("dashed",
+                "dotted","dotted","dotted",
+                "solid")
+
 Theme_special<-function()
 {
-  theme(axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
+  theme(legend.key.width=unit(1.2,"cm"),
+        axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
         axis.text.y = element_text(color = "black",size=12), #, vjust = 0.5, hjust=1
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
-  scale_color_manual(values=Colors_mMSE)+
+  #geom_point(size=1.75)+
+  geom_line(size=1)+
+  scale_color_manual(values=Colors_mVc)+
+  scale_linetype_manual(values=LineType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "r1_SMSE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = "r1_SMSE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 16)
+  ggexport(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "r1_ACCURACY_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "r1_ACCURACY_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mMSE.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mVc.pdf",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 12)
 
 ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggsave(filename = "r1_SMSE_MI_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Nor_mMSE.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
-  ggsave(filename = "r1_SMSE_MI_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
+  ggsave(filename = here("Article_Plots","r1_SMSE_MI_PR_TV_Nor_mVc.eps"),device="eps",dpi=300,width = 12,height = 16)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggsave(filename = "r1_ACCURACY_PR_TV_Nor_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Nor_mMSE.eps"),device="eps",dpi=300,width = 12,height = 12)
 ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggsave(filename = "r1_ACCURACY_PR_TV_Nor_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
+  ggsave(filename = here("Article_Plots","r1_ACCURACY_PR_TV_Nor_mVc.eps"),device="eps",dpi=300,width = 12,height = 12)
 
 ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mMSE.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Nor_mMSE.eps"),res=300,width = 12,height = 12)
 ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
-  ggexport(filename = "r1_SMSE_for_MLE_MI_PR_TV_Nor_mVc.eps",res=300,width = 12,height = 12)
+  ggexport(filename = here("Article_Plots","r1_SMSE_for_MLE_MI_PR_TV_Nor_mVc.eps"),res=300,width = 12,height = 12)
 ```

### 2023-02-15 Articles.Rmd
complex models included in the plot for articles rmarkdown

@@
 Old_Labels<-c("Real Model",paste0("Assumed Model ",1:3))
-New_Labels<-c("DM",paste0("AM ",1:3))
+New_Labels<-c("DM",paste0("AM ",1:2), "CM")
 
@@
 Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
-New_Labels<-c("DM",paste0("AM ",1:3),"MR")
+New_Labels<-c("DM",paste0("AM ",1:2), "CM","MR")
 
@@
 Identical_ro$Model<-factor(Identical_ro$Model,
-                           levels = c("RS DM","RS AM 1","RS AM 2","RS AM 3",
-                                      "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
+                           levels = c("RS DM","RS AM 1","RS AM 2","RS AM 3","RS CM",
+                                      "mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3","mMSE CM",
+                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3","mVc CM",
                                       "mMSE MR","mVc MR"))
@@
                                   `RS AM 3`="Random Sampling: Incorrect Model 3",
+                                  `RS CM` = "Random Sampling: Complex Model",
                                   `mMSE DM`="Optimal subsampling mMSE: Data Model",
@@
                                   `mMSE AM 3`="Optimal subsampling mMSE: Incorrect Model 3",
+                                  `mMSE CM` = "Optimal subsampling mMSE: Complex Model",
                                   `mVc DM`="Optimal subsampling mVc: Data Model",
@@
                                   `mVc AM 3`="Optimal subsampling mVc: Incorrect Model 3",
+                                  `mVc CM`="Optimal subsampling mVc: Complex Model",
                                   `mMSE MR`="Model Robust subsampling mMSE: Data Model",
@@
                         "Optimal subsampling mMSE: Incorrect Model 3",
+                        "Optimal subsampling mMSE: Complex Model",
                         "Model Robust subsampling mMSE: Data Model")
@@
               "#cc0000", 
-              "#ff578a","#ff578a","#ff578a",
+              "#ff578a","#ff578a","#ff578a","#603BDE",
               "darkgreen")
@@
                  "dashed",
-                 "dotted","dotted","dotted",
+                 "dotted","dotted","dotted","dotdash",
                  "solid")
+
+ShapeType_mMSE<-c(16,
+                  1,
+                  4,4,4,3,
+                  8)
 
@@
                        "Optimal subsampling mVc: Incorrect Model 3",
+                       "Optimal subsampling mVc: Complex Model",
                        "Model Robust subsampling mVc: Data Model")
@@
                 "dashed",
-                "dotted","dotted","dotted",
+                "dotted","dotted","dotted","dotdash",
                 "solid")
+
+ShapeType_mVc<-c(16,
+                 1,
+                 4,4,4,3,
+                 8)
 
@@
 {
-  theme(legend.key.width=unit(1.2,"cm"),
+  theme(legend.key.width=unit(1,"cm"),
         axis.text.x = element_text(color = "black",size=12, angle = 45, hjust=0.75), #, vjust = 0.5
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  #geom_point(size=1.75)+
-  geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE
+  theme_bw()+guides(colour = guide_legend(nrow = 3))+Theme_special()->Temp_plot_mMSE
 
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  #geom_point(size=1.75)+
-  geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
@@
   scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
-  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc
+  theme_bw()+guides(colour = guide_legend(nrow = 3))+Theme_special()->Temp_plot_mVc
 
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="Average MSE Y" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mMSE)+
   scale_linetype_manual(values=LineType_mMSE)+
+  scale_shape_manual(values = ShapeType_mMSE)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
@@
 Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
-  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model))+
+  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model,linetype=Model,shape=Model))+
   scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                      breaks = unique(Identical_ro$Subsample_Size))+
-  geom_point(size=1.75)+geom_line(size=1)+
+  geom_point(size=1.25)+geom_line(size=0.75)+
   scale_color_manual(values=Colors_mVc)+
   scale_linetype_manual(values=LineType_mVc)+
+  scale_shape_manual(values = ShapeType_mVc)+
   facet_wrap(~Covariate,scales = "free_y",ncol = 2)+

### 2023-02-15 r1_Articles.Rmd
complex models included in the plot for articles rmarkdown

@@
 Old_Labels<-c("Real",paste0("Assumed Old ",1:3),"Model Free")
-New_Labels<-c("DM",paste0("AM ",1:3),"MR")
+New_Labels<-c("DM",paste0("AM ",1:2),"CM","MR")
 
@@
 Identical_ro$Model<-factor(Identical_ro$Model,
-                           levels = c("mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3",
-                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3",
+                           levels = c("mMSE DM","mMSE AM 1","mMSE AM 2","mMSE AM 3","mMSE CM",
+                                      "mVc DM","mVc AM 1","mVc AM 2","mVc AM 3","mVc CM",
                                       "mMSE MR","mVc MR"))
@@
 Colors_mMSE<-c("#cc0000", 
-               "#ff578a","#ff578a","#ff578a",
+               "#ff578a","#ff578a","#ff578a","#603BDE",
                "darkgreen")
@@
 LineType_mMSE<-c("dashed",
-                 "dotted","dotted","dotted",
+                 "dotted","dotted","dotted","dotdash",
                  "solid")
+
+ShapeType_mMSE<-c(1,
+                  4,4,4,3,
+                  8)
 
@@
 Colors_mVc<-c("#cc0000", 
-              "#ff578a","#ff578a","#ff578a",
+              "#ff578a","#ff578a","#ff578a","#603BDE",
               "darkgreen")
@@
 LineType_mVc<-c("dashed",
-                "dotted","dotted","dotted",
+                "dotted","dotted","dotted","dotdash",
                 "solid")
+
+ShapeType_mVc<-c(1,
+                 4,4,4,3,
+                 8)
 

### 2023-02-16 Articles.Rmd
facets and x axis corrected

@@
                                           "Data Model: x\u2081, x\u2082, (x\u2082)\u00B2",
-                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"))
+                                          "Data Model: x\u2081, x\u2082, (x\u2081)\u00B2, (x\u2082)\u00B2"),
+                               labels = c(expression("Data Model: "*X[1]*", "*X[2]),
+                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[1]^{2}),
+                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[2]^{2}),
+                                          expression("Data Model: "*X[1]*", "*X[2]*", "*X[1]^{2}*", "*X[2]^{2})))
 
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
   xlab("r")+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
   xlab("r")+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
   xlab("r")+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
   xlab("r")+

### 2023-02-16 r1_Articles.Rmd
facets and x axis corrected

@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 4,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("Average Model Information")+expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average Model Information)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average Model Information)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(SMSE)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(SMSE)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mMSE)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+
@@
   scale_shape_manual(values = ShapeType_mVc)+
-  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
-  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
+  facet_wrap(~Covariate,scales = "free_y",ncol = 2,labeller = label_parsed)+
+  xlab(expression(paste(r[0],'+ r = 1000 and ',r[0])))+
   ylab("log(Average MSE of Y)")+#expand_limits(y = 0)+

### 2023-02-18 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Setup.R
New probability updated with Correct matrix

@@ -89,18 +89,18 @@ Run_OSMAC<-function(Replicates,r1,r2,Y,X,Real_Data,N,alpha,combs,All_Covariates)
       
       Bias_Assumed_Old_mMSE_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mMSE
       Bias_Assumed_Old_mVc_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mVc
-      Bias_Assumed_New_mMSE_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mMSE
-      Bias_Assumed_New_mVc_1[[i]]<-Results$opt$opt_Old$opt_Old_1$Bias_mVc
+      Bias_Assumed_New_mMSE_1[[i]]<-Results$opt$opt_New$opt_New_1$Bias_mMSE
+      Bias_Assumed_New_mVc_1[[i]]<-Results$opt$opt_New$opt_New_1$Bias_mVc
       
       Bias_Assumed_Old_mMSE_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mMSE
       Bias_Assumed_Old_mVc_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mVc
-      Bias_Assumed_New_mMSE_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mMSE
-      Bias_Assumed_New_mVc_2[[i]]<-Results$opt$opt_Old$opt_Old_2$Bias_mVc
+      Bias_Assumed_New_mMSE_2[[i]]<-Results$opt$opt_New$opt_New_2$Bias_mMSE
+      Bias_Assumed_New_mVc_2[[i]]<-Results$opt$opt_New$opt_New_2$Bias_mVc
       
       Bias_Assumed_Old_mMSE_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mMSE
       Bias_Assumed_Old_mVc_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mVc
-      Bias_Assumed_New_mMSE_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mMSE
-      Bias_Assumed_New_mVc_3[[i]]<-Results$opt$opt_Old$opt_Old_3$Bias_mVc
+      Bias_Assumed_New_mMSE_3[[i]]<-Results$opt$opt_New$opt_New_3$Bias_mMSE
[…]

### 2023-02-27 Articles.Rmd
updated model information for all simulations

@@
 
-ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 16)
-ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
-  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 16)
+# ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
+#   ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 16)
+ggarrange(p3,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
+  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mMSE.pdf"),res=300,width = 12,height = 12)
+# ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
+#   ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 16)
+ggarrange(p4,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
+  ggexport(filename = here("Article_Plots","SMSE_MI_PR_TV_Nor_mVc.pdf"),res=300,width = 12,height = 12)
 ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%

### 2023-02-27 Identical_r0/Rmarkdown/OSMAC_Command.R

@@ -4,19 +4,19 @@ library(rmarkdown)
 Model<-c("Model_1","Model_2",
          "Model_3","Model_4") ; j=4
 
-for (j in 1:length(Model)) 
+for (jj in 1:length(Model)) 
 {
   # OSMAC Method ----
   render(input=here("Identical_r0","Rmarkdown","OSMAC_Method.Rmd"),
          output_format = "html_document",
          output_file = "OSMAC_Method",
-         output_dir=here("Identical_r0","htmloutputs",Model[j],"OSMAC"),
-         params=list("Model_Path"=Model[j]))
+         output_dir=here("Identical_r0","htmloutputs",Model[jj],"OSMAC"),
+         params=list("Model_Path"=Model[jj]))
   
-  render(input=here("Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
-         output_format = "html_document",
-         output_file = "r1_OSMAC_Method",
-         output_dir=here("Identical_r0","htmloutputs",Model[j],"OSMAC"),
-         params=list("Model_Path"=Model[j]))
+  # render(input=here("Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_OSMAC_Method",
+  #        output_dir=here("Identical_r0","htmloutputs",Model[jj],"OSMAC"),
+  #        params=list("Model_Path"=Model[jj]))
 }
 

### 2023-02-27 Identical_r0/Rmarkdown/Summary/Summary_Rmarkdown.R

@@ -5,18 +5,18 @@ Model<-c("Model_1","Model_2",
          "Model_3","Model_4"); i=4
 
 # Best_Subsampling_Method ----
-for (i in 1:length(Model))
+for (ii in 1:length(Model))
 {
-  # render(input=here("Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
-  #        output_format = "html_document",
-  #        output_file = "Best_Subsampling_Method",
-  #        output_dir=here("Identical_r0","Summary",Model[i],"Best_Subsampling"),
-  #        params=list("Model_Path"=Model[i]))
-  
-  render(input=here("Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+  render(input=here("Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
          output_format = "html_document",
-         output_file = "r1_Best_Subsampling_Method",
-         output_dir=here("Identical_r0","Summary",Model[i],"Best_Subsampling"),
-         params=list("Model_Path"=Model[i]))
+         output_file = "Best_Subsampling_Method",
+         output_dir=here("Identical_r0","Summary",Model[ii],"Best_Subsampling"),
+         params=list("Model_Path"=Model[ii]))
+  
+  # render(input=here("Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_Best_Subsampling_Method",
+  #        output_dir=here("Identical_r0","Summary",Model[ii],"Best_Subsampling"),
+  #        params=list("Model_Path"=Model[ii]))
 }
 

### 2023-02-27 Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two step OSMAC ----
-AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates,Theta){
     Y_Real<-Real_Data[,1] #  Real Data
     X_Real<-Real_Data[,-1] # Real Data
     
@@ -249,7 +249,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
       V_Temp<-t(x_Real.mVc)%*% (x_Real.mVc * ((as.vector(y_Real.mVc)-pi)* pinv_Real.mVc)^2)   
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mVc_Real[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<- c(exp(x_Real.mVc %*% Theta))
+      Mx_1<-t(x_Real.mVc) %*% (x_Real.mVc * pi_1)
+      
+      Utility_mVc_Real[i,]<-cbind(r2[i],tr(V_Final),det(Mx_1))
       Bias_mVc_Real[i,]<-Cordeiro(XData=x_Real.mVc,With_bias = beta.mVc_Real[i,])
       
       # Assumed Data Old probabilities
@@ -274,9 +277,17 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,n,Real_Data,alpha,combs,All_Covariates){
         Mx[[a]] %*% V_Temp[[a]] %*% Mx[[a]]
       }) 
       
+      pi_1<- lapply(1:length(combs), function(a){
+        c(exp(x_Assumed.mVc[[a]] %*% Theta))
+      })
+      
+      Mx_1<-lapply(1:length(combs),function(a){
+        t(x_Assumed.mVc[[a]]) %*% (x_Assumed.mVc[[a]] * pi_1[[a]]) 
+      })
+      
       for (j in 1:length(combs)) 
       {
-        Utility_mVc_Old[[j]][i,]<-cbind(r2[i],tr(V_Final[[j]]),det(solve(V_Final[[j]])))
[…]

### 2023-02-27 Non_Identical_r0/Rmarkdown/Random_Sampling_And_OSMAC.R

@@ -4,39 +4,39 @@ library(rmarkdown)
 Model<-c("Model_1","Model_2",
          "Model_3","Model_4") ; j=1
 
-for (j in 1:length(Model)) 
+for (jj in 1:length(Model)) 
 {
   # Random Sampling ----
   render(input = here("Non_Identical_r0","Rmarkdown","Random_Sampling.Rmd"),
          output_format = "html_document",
          output_file = "Random_Sampling",
-         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"Random_Sampling"),
-         params = list("Model_Path"=Model[j]))
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[jj],"Random_Sampling"),
+         params = list("Model_Path"=Model[jj]))
   
   # OSMAC Method ----
   render(input = here("Non_Identical_r0","Rmarkdown","OSMAC_Method.Rmd"),
          output_format = "html_document",
          output_file = "OSMAC_Method",
-         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
-         params = list("Model_Path"=Model[j]))
+         output_dir = here("Non_Identical_r0","htmloutputs",Model[jj],"OSMAC"),
+         params = list("Model_Path"=Model[jj]))
   
-  render(input = here("Non_Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
-         output_format = "html_document",
-         output_file = "r1_OSMAC_Method",
-         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC"),
-         params = list("Model_Path"=Model[j]))
+  # render(input = here("Non_Identical_r0","Rmarkdown","r1_OSMAC_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_OSMAC_Method",
+  #        output_dir = here("Non_Identical_r0","htmloutputs",Model[jj],"OSMAC"),
+  #        params = list("Model_Path"=Model[jj]))
   
   # OSMAC Model Free Method ----
   render(input = here("Non_Identical_r0","Rmarkdown","OSMAC_Model_Free_Method.Rmd"),
          output_format = "html_document",
          output_file = "OSMAC_Model_Free_Method",
-         output_dir = here("Non_Identical_r0","htmloutputs",Model[j],"OSMAC_Model_Free"),
-         params = list("Model_Path"=Model[j]))
[…]

### 2023-02-27 Non_Identical_r0/Rmarkdown/Summary/Summary_Rmarkdown.R

@@ -5,18 +5,18 @@ Model<-c("Model_1","Model_2",
          "Model_3","Model_4"); i=4
 
 # Best_Subsampling_Method ----
-for (i in 1:length(Model))
+for (ii in 1:length(Model))
 {
-  # render(input=here("Non_Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
-  #        output_format = "html_document",
-  #        output_file = "Best_Subsampling_Method",
-  #        output_dir=here("Non_Identical_r0","Summary",Model[i],"Best_Subsampling"),
-  #        params=list("Model_Path"=Model[i]))
-  
-  render(input=here("Non_Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+  render(input=here("Non_Identical_r0","Rmarkdown","Summary","Best_Subsampling_Method.Rmd"),
          output_format = "html_document",
-         output_file = "r1_Best_Subsampling_Method",
-         output_dir=here("Non_Identical_r0","Summary",Model[i],"Best_Subsampling"),
-         params=list("Model_Path"=Model[i]))
+         output_file = "Best_Subsampling_Method",
+         output_dir=here("Non_Identical_r0","Summary",Model[ii],"Best_Subsampling"),
+         params=list("Model_Path"=Model[ii]))
+  
+  # render(input=here("Non_Identical_r0","Rmarkdown","Summary","r1_Best_Subsampling_Method.Rmd"),
+  #        output_format = "html_document",
+  #        output_file = "r1_Best_Subsampling_Method",
+  #        output_dir=here("Non_Identical_r0","Summary",Model[ii],"Best_Subsampling"),
+  #        params=list("Model_Path"=Model[ii]))
 }
 

### 2023-02-27 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC/Simulation_Results_OSMAC_Sampling.R

@@ -18,7 +18,8 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
                            Y=as.matrix(Simulated_Data[[2]]$Real_Model[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Real_Model[,-1]),
                            Real_Data=as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N,Model="Real_Model")
+                           N=Simulated_Data$Basic$N,Model="Real_Model",
+                           Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 1 ----
 # Generate for Random sample of 1000 different times ---
@@ -27,7 +28,8 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
                            Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Assumed_Model_1[,-1]),
                            Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1")
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_1",
+                           Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 2 ----
 # Generate for Random sample of 1000 different times ---
@@ -36,7 +38,8 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
                            Y=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,1]),
                            X=as.matrix(Simulated_Data[[2]]$Assumed_Model_2[,-1]),
                            Real_Data = as.matrix(Simulated_Data[[2]]$Real_Model),
-                           N=Simulated_Data$Basic$N, Model="Assumed_Model_2")
+                           N=Simulated_Data$Basic$N, Model="Assumed_Model_2",
+                           Theta=Simulated_Data$Basic$Theta)
 
 # Assumed Model 3 ----
 # Generate for Random sample of 1000 different times ---
@@ -45,4 +48,5 @@ Final_Parameter<-Run_OSMAC(Replicates=Replicates,r1=r0,r2=c(100*(2:15)),
[…]

### 2023-02-27 Non_Identical_r0/Simulation_Setup/Analysis/OSMAC_Model_Free/Simulation_Results_OSMAC_Sampling.R

@@ -29,7 +29,8 @@ if(Model_Path=="Model_1")
                                 X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,
+                                Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 2 ----
@@ -48,7 +49,8 @@ if(Model_Path=="Model_2")
                                 X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,
+                                Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 3 ----
@@ -66,7 +68,8 @@ if(Model_Path=="Model_3")
                                 X=as.matrix(Simulated_Data[[2]]$Assumed_Model_3[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,
+                                Theta=Simulated_Data$Basic$Theta)
 }
 
 # Model 4 ----
@@ -84,5 +87,6 @@ if(Model_Path=="Model_4")
                                 X=as.matrix(Simulated_Data[[2]]$Real_Model[,-1]),
                                 alpha = rep(1/4,length(combs)), N=Simulated_Data$Basic$N,
                                 All_Covariates=All_Covariates,
-                                combs=combs)
+                                combs=combs,
+                                Theta=Simulated_Data$Basic$Theta)
 }

### 2023-02-27 Non_Identical_r0/Simulation_Setup/Analysis/Random_Sampling/Simulation_Results_Random_Sampling.R

@@ -17,7 +17,8 @@ Final_Parameter<-Run_RandomSample(Replicates = Replicates,
                                   FullData = Simulated_Data[[2]]$Real_Model,
                                   N=Simulated_Data$Basic$N,
                                   Subsample_Size=Subsample_Size,Choices=c(100*(2:15)),
-                                  No_of_Models = 4)
+                                  No_of_Models = 4,
+                                  Theta=Simulated_Data$Basic$Theta)
 
 Est_Param_RandomSample<-Final_Parameter$EstPar[[1]]
 Utility_RandomSample<-Final_Parameter$Utility[[1]]

### 2023-02-27 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Algorithm.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two step OSMAC ----
-AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
+AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model,Theta) {
   if(Model=="Real_Model")
   {
     PI.prop <- rep(1/n, n)
@@ -69,7 +69,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mVc[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<- c(exp(x.mVc %*% Theta))
+      Mx_1<-t(x.mVc) %*% (x.mVc * pi_1 )
+      
+      Utility_mVc[i,]<-cbind(r2[i],tr(V_Final),det(Mx_1))
       Bias_mVc[i,]<-Cordeiro(XData=x.mVc,With_bias = beta.mVc[i,])
       
       ## mMSE
@@ -90,7 +93,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mMSE[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<-c(exp(x.mMSE %*% Theta))
+      Mx_1<-t(x.mMSE) %*% (x.mMSE * pi_1)
+      
+      Utility_mMSE[i,]<-cbind(r2[i],tr(V_Final),det(Mx_1))
       Bias_mMSE[i,]<-Cordeiro(XData=x.mMSE,With_bias = beta.mMSE[i,])
     }
     
@@ -165,7 +171,10 @@ AlgTwoStp <- function(r1=r1, r2=r2,Y,X,Real_Data,n,Model) {
       
       V_Final<-Mx %*% V_Temp %*% Mx
       
-      Utility_mVc[i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final)))
+      pi_1<- c(exp(x_Real.mVc %*% Theta))
+      Mx_1<-t(x_Real.mVc) %*% (x_Real.mVc * pi_1)
+      
[…]

### 2023-02-27 Non_Identical_r0/Simulation_Setup/R_Scripts/OSMAC_Model_Free/OSMAC_Algorithm_Model_Free.R

@@ -13,7 +13,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Two Step OSMAC ----
-OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates) 
+OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates,Theta) 
 {
   PI.prop <- rep(1/n, n)
   idx.prop <- sample(1:n, r1, T, PI.prop)
@@ -111,6 +111,11 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates)
       Utility_mVc[[j]][i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final))) #
     }
     
+    pi_1 <- c(exp(X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ] %*% Theta))
+    Mx_1 <- t(X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ]) %*% 
+      (X[c(idx.mVc, idx.prop),All_Covariates %in% combs[[1]] ] * pi_1)
+    Utility_mVc[[1]][i,3]<-det(Mx_1) #
+    
     ## mMSE
     idx.mMSE <- sample(1:n, r2[i]-r1, T, pjoin.mMSE)
     
@@ -143,6 +148,11 @@ OSMAC_MF <- function(r1,r2,Y,X,n,alpha,combs,All_Covariates)
       
       Utility_mMSE[[j]][i,]<-cbind(r2[i],tr(V_Final),det(solve(V_Final))) #
     }
+    pi_1 <-c(exp(X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ] %*% Theta)) #
+    Mx_1<- solve(t(X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ]) %*% 
+                  (X[c(idx.mMSE, idx.prop),All_Covariates %in% combs[[1]] ] * pi_1)) 
+    Utility_mMSE[[1]][i,3]<-det(Mx_1) #
+    
   }
   
   #Sample_mVc<-do.call(rbind,Sample.mVc) #

### 2023-02-27 Non_Identical_r0/Simulation_Setup/R_Scripts/Random_Sampling_Setup.R

@@ -17,7 +17,7 @@ Cordeiro<-function(XData,With_bias)
 }
 
 # Using Random Sampling Sub-sample from Big Data ----
-Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_Models)
+Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_Models,Theta)
 {
   #RandomSample<-list()
   #Sample_RS<-list()
@@ -47,7 +47,11 @@ Run_RandomSample <- function(Replicates,FullData,Subsample_Size,N,Choices,No_of_
         Temp_Temp_Data<-Temp_Data[1:Choices[j],]
         Results<-glm(Y~.-1,data=Temp_Temp_Data,family = "poisson")
         Est_Parameter[j,]<-c(Choices[j],Results$coefficients)
-        optimality[j,]<-c(Choices[j], psych::tr(vcov(Results)), det(solve(summary(Results)$cov.unscaled)) )
+        
+        pi_1<-c(exp(as.matrix(Temp_Temp_Data[,-1]) %*% Theta))
+        Mx_1<-t(as.matrix(Temp_Temp_Data[,-1])) %*% (as.matrix(Temp_Temp_Data[,-1]) * pi_1)
+        
+        optimality[j,]<-c(Choices[j], psych::tr(vcov(Results)), det(Mx_1))
         Bias[j,]<-c(Choices[j],Cordeiro(XData = as.matrix(Temp_Temp_Data[,-1]),
                                         With_bias = as.vector(Results$coefficients)))
       }

### 2023-02-27 Publication_Ready_command.R

@@ -4,18 +4,18 @@ library(rmarkdown)
 Model<-c("Model_1","Model_2",
          "Model_3","Model_4"); i=1
 
-for(i in 1:length(Model))
+for(ii in 1:length(Model))
 {
   # Publication Ready ----
-  # render(input=here("Publication_Ready.Rmd"),
-  #        output_format = "github_document",
-  #        output_file = "Publication_Ready",
-  #        output_dir=here("Publication_Ready",Model[i]),
-  #        params=list("Model_Path"=Model[i]))
-  
-  render(input=here("r1_Publication_Ready.Rmd"),
+  render(input=here("Publication_Ready.Rmd"),
          output_format = "github_document",
-         output_file = "r1_Publication_Ready",
-         output_dir=here("Publication_Ready",Model[i]),
-         params=list("Model_Path"=Model[i]))
+         output_file = "Publication_Ready",
+         output_dir=here("Publication_Ready",Model[ii]),
+         params=list("Model_Path"=Model[ii]))
+  
+  # render(input=here("r1_Publication_Ready.Rmd"),
+  #        output_format = "github_document",
+  #        output_file = "r1_Publication_Ready",
+  #        output_dir=here("Publication_Ready",Model[ii]),
+  #        params=list("Model_Path"=Model[ii]))
 }

### 2023-03-05 Manual.Rmd
Manual updated after removing classical folder from the chain

@@
 1. Random Sampling, 
-2. Rare event random sampling, 
-3. Optimal Sub-sampling (OSMAC), and
-4. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).
+2. Optimal Sub-sampling (OSMAC), and
+3. Model Robust Optimal Sub-sampling (OSMAC_MF or OSMAC Model Free).
 
@@
 
-### 2.2.1 Classical/R_Scripts
+### 2.2.1 R_Scripts
 
@@
 
-* Data stored in **Generate_Big_Data** is transferred to **Classical/Analysis**.
+* Data stored in **Generate_Big_Data** is transferred to **Analysis**.
 
@@
 
-#### 2.2.1.3 RE Random_Sampling_Setup.R
-
-* A setup for rare event random sampling such that model parameters and model information are estimated at each simulation and are applied for the generated big data.
-
-#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]
+#### 2.2.1.3 OSMAC_Algorithm.R and OSMAC_Setup.R [Identical r0]
 
@@
 
-#### 2.2.1.5 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]
+#### 2.2.1.4 OSMAC_Algorithm.R and OSMAC_Setup.R [Non Identical r0]
 
@@
 
-#### 2.2.1.6 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]
+#### 2.2.1.5 OSMAC_Algorithm_Model_Free.R and OSMAC_Model_Free_Setup.R [Non_Identical_r0]
 
@@
 
-## 2.2.2 Classical/Analysis
+## 2.2.2 Analysis
 
@@
 
-#### 2.2.2.2 RE Random Sampling
-
-* **Init.RData** - data file containing the generated big data and initial information regarding the simulation.
-* **RE_RandomSample.RData** - RE Random sampling function for **Replicates**.
-* **Simulation_Results_RE_Random_Sampling.R** - R script to run the rare event random sampling method over **Replicates** on the **Init.RData** from **RE_RandomSample.RData**.
-* **Results** - Results of the simulation are stored here according to real and assumed models, in each folder a single Rdata file **RE_Random_Sample_output.RData** is stored.
-
-#### 2.2.2.3 OSMAC [Non Identical r0]
+#### 2.2.2.2 OSMAC [Non Identical r0]
 
@@
 
-#### 2.2.2.4 OSMAC Model Free [Non Identical r0]
+#### 2.2.2.3 OSMAC Model Free [Non Identical r0]
 
@@
 
-#### 2.2.2.5 OSMAC [Identical r0]
+#### 2.2.2.4 OSMAC [Identical r0]
 
@@
 
-* **RE_and_Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.
+* **Random_Sampling_and_OSMAC.R** - R script to summarise the results from the sub-sampling methods through the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd**.
 
@@
 
-* **Summary_Rmarkdown.R** in the **Rmarkdown/Classical/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.
+* **Summary_Rmarkdown.R** in the **Rmarkdown/Summary** folder compares the sub-sampling methods through Mean Squared Error, variance and model information through the **Best_Subsampling_Method.Rmd**.
 
@@
 
-* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.
+* Here, summaries from the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd**(for Identical and Non Identical r0) and **OSMAC_Model_Free_Method.Rmd** (for Non Identical r0) are stored as html files.
 
@@
 
-### 2.6.1 Summary/Classical/Model_[1 or 2 or 3 or 4]/Data/Efficiency
+### 2.6.1 Summary/Model_[1 or 2 or 3 or 4]/Data/Efficiency
 
-* When running the Rmarkdown files **Random_Sampling.Rmd**, **RE_Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.
+* When running the Rmarkdown files **Random_Sampling.Rmd**, **OSMAC_Method.Rmd** and **OSMAC_Model_Free_Method.Rmd** summary data (MSE and model information) are stored here.
 
-* Using these data files only summarising through the files in **Rmarkdown/Classical/Summary** occurs.
+* Using these data files only summarising through the files in **Rmarkdown/Summary** occurs.
 
@@
 
-* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **SMSE_MI_PR_TV_Nor_mMSE.pdf** and **SMSE_MI_PR_TV_Nor_mVc.pdf**.
+* Use **Articles.Rmd** to generate plots relevant to the paper as pdf files **Article_Plots/SMSE_MI_PR_TV_Nor_mMSE.pdf** and **Article_Plots/SMSE_MI_PR_TV_Nor_mVc.pdf**.
